### 2015-02-12 defense_pres.tex
Adds code for defense presentation.

\documentclass[20pt]{beamer}
\usetheme{Pittsburgh}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Elita Baldridge}
\title{A data-intensive assessment of the species-abundance distribution.
}
%\setbeamercovered{transparent} 
%\logo{} 
%\institute{} 
%\subject{} 
\begin{document}

\begin{frame}
\titlepage
\end{frame}

%\begin{frame}
%\tableofcontents
%\end{frame}

\begin{frame}{•}

\end{frame}

\end{document}

### 2015-02-13 sad_comparison_functions.py
Simplify get_sample_multi_dists() using a dictionary.

@@ -7,6 +7,13 @@ import scipy.stats.distributions as sd
 import mete
 import csv
 
+# Define dictionary to match names to distributions
+DIST_DIC = {'logser': sd.logser,
+            'geom': sd.geom,
+            'zipf': sd.zipf,
+            'negbin': md.nbinom_lower_trunc,
+            'pln': md.pln}
+
 def import_abundance(datafile):
     """Imports raw species abundance .csv files in the form: Site, Year, Species, Abundance."""
     raw_data = np.genfromtxt(datafile, dtype = "S30,i8,S30,i8", names = ['site','year','sp','ab'], delimiter = ",",comments = "#")
@@ -49,22 +56,28 @@ def get_pred_iterative(cdf_obs, dist, *pars):
                 return np.array(abundance)
         i += 1
 
-def get_sample_multi_dists(S, dist_name, pars):
+def get_sample_multi_dists(S, dist_name, *pars):
     """Returns a random sample of length S from the designated distribution."""
-    dist = 0
-    if dist_name == 'logser': dist = sd.logser
-    elif dist_name == 'geom': dist = sd.geom
-    elif dist_name == 'zipf': dist = sd.zipf
-    if dist:
-        rand_smp = dist.rvs(pars, size = S)
-    else:
-        if dist_name == 'negbin':
-            n, p = pars
-            rand_smp = md.nbinom_lower_trunc.rvs(n, p, size = S)
-        elif dist_name == 'pln':
-            mu, sigma = pars
-            rand_smp = md.pln.rvs(mu, sigma, True, size = S)
+    dist = DIST_DIC[dist_name]
+    if dist_name == 'pln': pars += (True, )
+    rand_smp = dist.rvs(*pars, size = S)
     return rand_smp
+#def get_sample_multi_dists(S, dist_name, pars):
+    #"""Returns a random sample of length S from the designated distribution."""
+    #dist = 0
+    #if dist_name == 'logser': dist = sd.logser
+    #elif dist_name == 'geom': dist = sd.geom
+    #elif dist_name == 'zipf': dist = sd.zipf
+    #if dist:
+        #rand_smp = dist.rvs(pars, size = S)
+    #else:
+        #if dist_name == 'negbin':
+            #n, p = pars
+            #rand_smp = md.nbinom_lower_trunc.rvs(n, p, size = S)
+        #elif dist_name == 'pln':
+            #mu, sigma = pars
[…]

### 2015-02-13 sad_comparison_functions.py
Simplify get_loglik_multi_dists().

@@ -62,22 +62,6 @@ def get_sample_multi_dists(S, dist_name, *pars):
     if dist_name == 'pln': pars += (True, )
     rand_smp = dist.rvs(*pars, size = S)
     return rand_smp
-#def get_sample_multi_dists(S, dist_name, pars):
-    #"""Returns a random sample of length S from the designated distribution."""
-    #dist = 0
-    #if dist_name == 'logser': dist = sd.logser
-    #elif dist_name == 'geom': dist = sd.geom
-    #elif dist_name == 'zipf': dist = sd.zipf
-    #if dist:
-        #rand_smp = dist.rvs(pars, size = S)
-    #else:
-        #if dist_name == 'negbin':
-            #n, p = pars
-            #rand_smp = md.nbinom_lower_trunc.rvs(n, p, size = S)
-        #elif dist_name == 'pln':
-            #mu, sigma = pars
-            #rand_smp = md.pln.rvs(mu, sigma, True, size = S)
-    #return rand_smp
 
 def get_pred_multi_dists(S, dist_name, pars):
     """Returns the predicted abundances given species richness, 
@@ -104,25 +88,15 @@ def get_pred_multi_dists(S, dist_name, pars):
         pred = None
     return pred
 
-def get_loglik_multi_dists(ab, dist_name, pars):
+def get_loglik_multi_dists(ab, dist_name, *pars):
     """Returns the log-likelihood given abundances, 
     
     the designated distribution, and the parameters.
     
     """
-    dist = 0
-    if dist_name == 'logser': dist = sd.logser
-    elif dist_name == 'geom': dist = sd.geom
-    elif dist_name == 'zipf': dist = sd.zipf
-    if dist: # If one of the above three cases:
-        loglik = sum(dist.logpmf(ab, pars))
-    else:
-        if dist_name == 'negbin':
-            n, p = pars
-            loglik = sum(np.log(md.nbinom_lower_trunc.pmf(ab, n, p)))
-        elif dist_name == 'pln':
-            mu, sigma = pars
-            loglik = sum(np.log(md.pln.pmf(ab, mu, sigma, True)))
+    dist = DIST_DIC[dist_name]
+    if dist_name == 'pln': pars += (True,)
+    loglik = sum(np.log(dist.pmf(ab, *pars)))
     return loglik
 
 def get_ks_multi_dists(ab, dist_name, pars):

### 2015-02-13 sad_comparison_functions.py
Simplify get_ks_multi_dists().

@@ -99,7 +99,7 @@ def get_loglik_multi_dists(ab, dist_name, *pars):
     loglik = sum(np.log(dist.pmf(ab, *pars)))
     return loglik
 
-def get_ks_multi_dists(ab, dist_name, pars):
+def get_ks_multi_dists(ab, dist_name, *pars):
     """Returns the K-S statistic given abundances, 
     
     the designated distribution, and the parameters.
@@ -107,19 +107,9 @@ def get_ks_multi_dists(ab, dist_name, pars):
     """
     ab = sorted(ab)
     emp_cdf = (np.arange(1, len(ab) + 1) - 0.5) / len(ab)  
-    dist = 0
-    if dist_name == 'logser': dist = sd.logser
-    elif dist_name == 'geom': dist = sd.geom
-    elif dist_name == 'zipf': dist = sd.zipf
-    if dist: # If one of the above three cases:
-        ks = max(abs(emp_cdf - np.array([dist.cdf(x, pars) for x in ab])))
-    else:
-        if dist_name == 'negbin':
-            n, p = pars
-            ks = max(abs(emp_cdf - np.array([md.nbinom_lower_trunc.cdf(x, n, p) for x in ab])))
-        elif dist_name == 'pln':
-            mu, sigma = pars
-            ks = max(abs(emp_cdf - np.array([md.pln.cdf(x, mu, sigma, True) for x in ab])))
+    dist = DIST_DIC[dist_name]
+    if dist_name == 'pln': pars += (True, )
+    ks = max(abs(emp_cdf - np.array([dist.cdf(x, *pars) for x in ab])))
     return ks
     
 def get_obs_pred_multi_dists(dat_dir, file_name, dist_name, cutoff = 9):

### 2015-02-13 sad_comparison_functions.py
Simplify get_pred_multi_dists().

@@ -63,7 +63,7 @@ def get_sample_multi_dists(S, dist_name, *pars):
     rand_smp = dist.rvs(*pars, size = S)
     return rand_smp
 
-def get_pred_multi_dists(S, dist_name, pars):
+def get_pred_multi_dists(S, dist_name, *pars):
     """Returns the predicted abundances given species richness, 
     
     the designated distribution, and the parameters.
@@ -71,21 +71,11 @@ def get_pred_multi_dists(S, dist_name, pars):
     """
     cdf = (np.arange(1, S + 1) - 0.5) / S
     cdf = cdf[::-1]
-    if dist_name == 'logser':
-        pred = get_pred_iterative(cdf, sd.logser, pars)
-    elif dist_name == 'pln':
-        mu, sigma = pars
-        pred = get_pred_iterative(cdf, md.pln, mu, sigma, True)
-    elif dist_name == 'geom':
-        pred = sd.geom.ppf(cdf, pars)
-    elif dist_name == 'negbin':
-        n, p = pars
-        pred = get_pred_iterative(cdf, md.nbinom_lower_trunc, n, p)
-    elif dist_name == 'zipf':
-        pred = get_pred_iterative(cdf, sd.zipf, pars)
-    else: 
-        print "Error: distribution not recognized."
-        pred = None
+    dist = DIST_DIC[dist_name]
+    if dist_name == 'pln': pars += (True, )
+    if dist_name == 'geom': pred = dist.ppf(cdf, *pars)
+    else:  # For all other distributions, need to call the iterative method
+        pred = get_pred_iterative(cdf, dist, *pars)
     return pred
 
 def get_loglik_multi_dists(ab, dist_name, *pars):

### 2015-02-13 defense_pres.tex
Removes obnoxious navigation symbols and date.
Adds weecology and Ecology Center logos.
Fiddles with logos.

@@
-\documentclass[20pt]{beamer}
+\documentclass[30pt]{beamer}
 \usetheme{Pittsburgh}
@@
 \author{Elita Baldridge}
-\title{A data-intensive assessment of the species-abundance distribution.
-}
+\title{A data-intensive assessment of the species-abundance distribution.}
+\setbeamertemplate{navigation symbols}{}
+\date{}
 %\setbeamercovered{transparent} 
-%\logo{} 
-%\institute{} 
+\logo{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
+%\institute{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
 %\subject{} 
@@
 
-\begin{frame}{•}
+\begin{frame}{}
 

### 2015-02-13 sad_comparison_functions.py
Modify sim_stats() accordingly wrt to previous changes.

@@ -23,17 +23,17 @@ def get_par_multi_dists(ab, dist_name):
     """Returns the parameters given the observed abundances and the designated distribution."""
     if dist_name == 'logser':
         beta = mete.get_beta(len(ab), sum(ab), version = 'untruncated')
-        par = np.exp(-beta)
+        par = (np.exp(-beta), )
     elif dist_name == 'pln':
         par = md.pln_solver(ab)
     elif dist_name == 'geom':
-        par = len(ab) / sum(ab)
+        par = (len(ab) / sum(ab), )
     elif dist_name == 'negbin':
         par = md.negbin_solver(ab)
         if np.isnan(par[0]):
             par = None
     elif dist_name == 'zipf':
-        par = md.zipf_solver(ab)
+        par = (md.zipf_solver(ab), )
     else: 
         print "Error: distribution not recognized."
         par = None    
@@ -114,7 +114,7 @@ def get_obs_pred_multi_dists(dat_dir, file_name, dist_name, cutoff = 9):
         if len(obs_site) > cutoff: 
             pars_dist_site = get_par_multi_dists(obs_site, dist_name)
             if pars_dist_site and (np.any(np.isnan(pars_dist_site)) == 0):  # The estimated parameters exist and are not NANs
-                pred_dist_site = get_pred_multi_dists(len(obs_site), dist_name, pars_dist_site)
+                pred_dist_site = get_pred_multi_dists(len(obs_site), dist_name, *pars_dist_site)
                 results = np.zeros((len(obs_site), ), dtype = ('S30, i8, i8'))
                 results['f0'] = np.array([site] * len(obs_site))
                 results['f1'] = obs_site
@@ -132,19 +132,20 @@ def sim_stats(ab, dist_name, Nsim, test_stat):
     Nsim - number of simulated abundance lists
     test_stat - can be either log-likelihood ('loglik'), Kolmogorov-Smirnov statistic ('ks'), or R^2 ('r2')
     Output: 
-    A list where the first element is the stat value for the empirical SAD and the remaining values are stats for the simulated SADs.
+    A list with two elements, where the first element is the output for empirical ab, 
+    and the second element is a list of length Nsim with the output for each simulated ab.
     
     """
     pars = get_par_multi_dists(ab, dist_name)
     if test_stat == 'loglik': test_func = get_loglik_multi_dists
     elif test_stat == 'ks': test_func = get_ks_multi_dists
[…]

### 2015-02-13 defense_pres.tex
Makes title larger by making the font size smaller through some magic I do not fully comprehend.

--- 2015-02-12 defense_pres.tex
@@
 \author{Elita Baldridge}
-\title{A data-intensive assessment of the species-abundance distribution.
-}
+\title{A data-intensive assessment of the species-abundance distribution.}
+\setbeamertemplate{navigation symbols}{}
+\date{}
 %\setbeamercovered{transparent} 
-%\logo{} 
-%\institute{} 
+%\logo{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
+\institute{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
 %\subject{} 

### 2015-02-13 defense_pres.tex
Changes font to serif font.
Makes ecology center and weecology logos bigger.

@@
-\documentclass[20pt]{beamer}
+\documentclass[17pt]{beamer}
 \usetheme{Pittsburgh}
 \usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amsfonts}
+\usepackage{mathptmx}
+\usepackage{tgbonum}
 \usepackage{amssymb}
 \usepackage{graphicx}
+\usefonttheme{structuresmallcapsserif}
+\usefonttheme{serif}
 \author{Elita Baldridge}
@@
 %\logo{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
-\institute{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
+\institute{\includegraphics[scale=.07]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.1]{../Miscellaneous/Pictures/Weecology.png}} 
 %\subject{} 

### 2015-02-16 sad_neutral_analysis.py
Changes default gray plotting background to white background.

@@ -84,6 +84,7 @@ else:
 
 sads = sads.dropna()
 sads['log_distinct_ab_vals'] = np.log(sads['distinct_ab_vals'])
+sns.set_style("whitegrid")
 ax = sns.lmplot('log_distinct_ab_vals', 'pln_aicc_wgt', data=sads, col='dataset', col_wrap=3,
                 hue='dataset', fit_reg=False)
 ax.set(xlabel="Distinct Abundance Values (log)", ylabel="AIC wgt for log-normal")

### 2015-02-16 sad_neutral_analysis.py
Adds comment to highlight graphing part of code.

@@ -82,6 +82,7 @@ else:
     sads.reset_index(inplace=True)
     sads.to_csv('./sad-data/chapter3/distribution_data.csv', index=False)
 
+# Create figure similar to figure 2b in the Connolly 2014 paper.
 sads = sads.dropna()
 sads['log_distinct_ab_vals'] = np.log(sads['distinct_ab_vals'])
 sns.set_style("whitegrid")

### 2015-02-17 defense_pres.tex
Adds graphs to presentation.

@@
-\documentclass[17pt]{beamer}
+\documentclass{beamer}
 \usetheme{Pittsburgh}
@@
 \author{Elita Baldridge}
-\title{A data-intensive assessment of the species-abundance distribution.}
+\title[17pt]{A data-intensive assessment of the species-abundance distribution.}
 \setbeamertemplate{navigation symbols}{}
@@
 \begin{frame}{}
+\includegraphics[scale=.5]{./sad-data/chapter2/bioregions.png}
+\end{frame}
 
+\begin{frame}{}
+\includegraphics[scale=.5]{./sad-data/chapter2/taxa_sites.png}
+\end{frame}
+
+\begin{frame}{}
+\includegraphics[scale=.5]{./sad-data/chapter2/num_taxa.png}
+\end{frame}
+
+\begin{frame}{}
+\includegraphics[scale=.5]{./sad-data/chapter1/AICc_weights.png}
+\end{frame}
+
+\begin{frame}{}
+\includegraphics[scale=.5]{./sad-data/chapter1/likelihoods.png}
+\end{frame}
+
+\begin{frame}{}
+\includegraphics[scale=.5]{./sad-data/chapter1/likelihoods_one_to_one.png}
+\end{frame}
+
+\begin{frame}{}
+\includegraphics[scale=.3]{./sad-data/chapter3/distabclasses_vs_lognormwgt.png}
 \end{frame}

### 2015-02-18 sad_neutral_analysis.py
Outputs new graph, makes points larger.

@@ -99,10 +99,11 @@ ax.savefig('./sad-data/chapter3/distabclasses_vs_lognormwgt.png')
 
 sads_by_dataset = sads.groupby('dataset').mean().reset_index()
 ax = sns.lmplot('log_distinct_ab_vals', 'pln_aicc_wgt', data=sads_by_dataset,
-                hue='dataset', fit_reg=False)
+                hue='dataset', fit_reg=False, scatter_kws={"s": 60, "alpha": 1})
 ax.set(xlabel="Distinct Abundance Values (log)", ylabel="AIC wgt for log-normal")
 ax.set(xlim=[np.log(5), np.log(300)], ylim=[0, 1])
 xticks = [10, 20, 50, 100, 200]
 ax.set(xticks=np.log(xticks))
 ax.set(xticklabels=xticks)
+ax.savefig('./sad-data/chapter3/avgvals_by_dataset.png')
 plt.show()

### 2015-03-15 sad_neutral_analysis.py
Tweaks legend.

@@ -130,7 +130,7 @@ datasets = ['bbs', 'cbc', 'fia', 'gentry', 'mcdb', 'naba'] # The rest of the dat
 data_dir = './sad-data/chapter1/'
 markers=['o', '^', 's','D','v', 'p']
 markersizes=3
-colors=["teal", 'c', "palegreen", "m", "gold", 'orchid']
+colors=["teal", 'c', "seagreen", "m", "gold", 'orchid']
 
 
 for i, dataset in enumerate(datasets):
@@ -143,16 +143,16 @@ for i, dataset in enumerate(datasets):
     
 
 #Make legend
-l1 = plt.scatter([],[], s=100, marker = 'o', facecolors='teal',  edgecolors='black')
-l3 = plt.scatter([],[], s=100, marker = '^', facecolors='c', edgecolors='black')
-l3 = plt.scatter([],[], s=100, marker = 's', facecolors='palegreen', edgecolors='black')
-l4 = plt.scatter([],[], s=100, marker = 'D', facecolors='m', edgecolors='black')
-l5 = plt.scatter([],[], s=100, marker = 'v', facecolors='gold', edgecolors='black')
-l3 = plt.scatter([],[], s=100, marker = 'p', facecolors='orchid', edgecolors='black')
+l1 = plt.scatter([],[], s=75, marker = 'o', facecolors='teal',  edgecolors='black')
+l3 = plt.scatter([],[], s=75, marker = '^', facecolors='c', edgecolors='black')
+l3 = plt.scatter([],[], s=75, marker = 's', facecolors='seagreen', edgecolors='black')
+l4 = plt.scatter([],[], s=75, marker = 'D', facecolors='m', edgecolors='black')
+l5 = plt.scatter([],[], s=75, marker = 'v', facecolors='gold', edgecolors='black')
+l3 = plt.scatter([],[], s=75, marker = 'p', facecolors='orchid', edgecolors='black')
 
 labels = ["BBS", "CBC", "FIA", "Gentry", "MCDB", "NABA"]
 
-leg = plt.legend([l1, l2, l3, l4, l5, l6], labels, frameon=False, fontsize=12, loc = 6, title='Datasets', scatterpoints = 1)
+leg = plt.legend([l1, l2, l3, l4, l5, l6], labels, frameon=False, fontsize=10, loc = 6, title='Datasets', scatterpoints = 1)
     
 plt.savefig('./sad-data/chapter3/partial_sites_map.png', dpi=250, pad_inches=0)
 plt.close()

### 2015-03-15 sad_neutral_analysis.py
Tweaks graph for additional data.

@@ -130,7 +130,7 @@ datasets = ['bbs', 'cbc', 'fia', 'gentry', 'mcdb', 'naba'] # The rest of the dat
 data_dir = './sad-data/chapter1/'
 markers=['o', '^', 's','D','v', 'p']
 markersizes=3
-colors=["teal", 'c', "seagreen", "m", "gold", 'orchid']
+colors=["teal", 'c', "seagreen", "m", "gold", 'palegreen']
 
 
 for i, dataset in enumerate(datasets):
@@ -143,16 +143,16 @@ for i, dataset in enumerate(datasets):
     
 
 #Make legend
-l1 = plt.scatter([],[], s=75, marker = 'o', facecolors='teal',  edgecolors='black')
-l3 = plt.scatter([],[], s=75, marker = '^', facecolors='c', edgecolors='black')
-l3 = plt.scatter([],[], s=75, marker = 's', facecolors='seagreen', edgecolors='black')
-l4 = plt.scatter([],[], s=75, marker = 'D', facecolors='m', edgecolors='black')
-l5 = plt.scatter([],[], s=75, marker = 'v', facecolors='gold', edgecolors='black')
-l3 = plt.scatter([],[], s=75, marker = 'p', facecolors='orchid', edgecolors='black')
+l1 = plt.scatter([],[], s=60, marker = 'o', facecolors='teal',  edgecolors='black')
+l2 = plt.scatter([],[], s=60, marker = '^', facecolors='c', edgecolors='black')
+l3 = plt.scatter([],[], s=60, marker = 's', facecolors='seagreen', edgecolors='black')
+l4 = plt.scatter([],[], s=60, marker = 'D', facecolors='m', edgecolors='black')
+l5 = plt.scatter([],[], s=60, marker = 'v', facecolors='gold', edgecolors='black')
+l6 = plt.scatter([],[], s=60, marker = 'p', facecolors='palegreen', edgecolors='black')
 
 labels = ["BBS", "CBC", "FIA", "Gentry", "MCDB", "NABA"]
 
-leg = plt.legend([l1, l2, l3, l4, l5, l6], labels, frameon=False, fontsize=10, loc = 6, title='Datasets', scatterpoints = 1)
+leg = plt.legend([l1, l2, l3, l4, l5, l6], labels, frameon=False, fontsize=8, loc = 6, scatterpoints = 1)
     
 plt.savefig('./sad-data/chapter3/partial_sites_map.png', dpi=250, pad_inches=0)
 plt.close()

### 2015-03-15 sad_neutral_analysis.py
Tweaks graph for better readability.

@@ -126,7 +126,7 @@ map = Basemap(projection='moll',lon_0=0,resolution='i') #Sets up map for Mollwei
 map.drawcoastlines(linewidth = .10)
 map.fillcontinents(color='black',lake_color='white')
 
-datasets = ['bbs', 'cbc', 'fia', 'gentry', 'mcdb', 'naba'] # The rest of the data do not have lat-longs.
+datasets = ['bbs', 'cbc', 'fia', 'naba', 'mcdb', 'gentry' ] # The rest of the data do not have lat-longs.
 data_dir = './sad-data/chapter1/'
 markers=['o', '^', 's','D','v', 'p']
 markersizes=3
@@ -139,7 +139,7 @@ for i, dataset in enumerate(datasets):
     longs = latlong_data["long"]
     x,y = map(longs,lats)
     map.plot(x,y, ls='', marker=markers[i], markeredgecolor= colors[i],
-    markeredgewidth=0.75, markersize=markersizes, fillstyle='none')
+    markeredgewidth=0.5, markersize=markersizes, fillstyle='none')
     
 
 #Make legend
@@ -150,7 +150,7 @@ l4 = plt.scatter([],[], s=60, marker = 'D', facecolors='m', edgecolors='black')
 l5 = plt.scatter([],[], s=60, marker = 'v', facecolors='gold', edgecolors='black')
 l6 = plt.scatter([],[], s=60, marker = 'p', facecolors='palegreen', edgecolors='black')
 
-labels = ["BBS", "CBC", "FIA", "Gentry", "MCDB", "NABA"]
+labels = ["BBS", "CBC", "FIA", "NABA", "MCDB", "Gentry"]
 
 leg = plt.legend([l1, l2, l3, l4, l5, l6], labels, frameon=False, fontsize=8, loc = 6, scatterpoints = 1)
     

### 2015-03-17 defense_pres.tex
Sets font color to match the blue in the USU Ecology Center logo.
Should set all the normal text to USU Blue also.
Works on presentation; adds frametitles.
Adds sections, subsections, and table.

@@
-\documentclass{beamer}
+\documentclass[17pt]{beamer}
 \usetheme{Pittsburgh}
+\usepackage{xcolor}
+\definecolor{USUBlue}{RGB}{26,57,89}
+\usecolortheme[named=USUBlue]{structure}
+\setbeamercolor{normal text}{fg=USUBlue}
 \usepackage[utf8]{inputenc}
@@
 \usefonttheme{serif}
+\setbeamercolor{author}{fg=USUBlue}
+\setbeamerfont{author}{size=\small}
+\setbeamerfont{frametitle}{size=\small}
 \author{Elita Baldridge}
@@
 
+\section{Data}
+
+\subsection{Compiled Data}
+\subsubsection{Data Collection}
+\begin{frame}[shrink=30]
+\frametitle{Data}
+\begin{table}
+\begin{tabular}{l|l} 
+ Variable name & Variable definitions\\ 
+\hline
+ Class & Taxonomic class of species \\
+ Family & Taxonomic family of species \\
+ Genus & Taxonomic genus of species\\
+ Species & Specific epithet of species  \\
+ Relative\_abundance & Relative abundance of species \\
+ Abundance & Abundance of species \\
+ Collection\_Year & Start of collecting \\
+ End\_Collection & End of collecting \\
+ Site\_Name & Name/description of site \\
+ Biogeographic\_region & Biogeographic region \\
+ Site\_notes & Additional site information \\ 
+\end{tabular}
+\caption{List of variables collected.}
+\end{table}
+\end{frame}
+
+\subsubsection{Data Summary}
 \begin{frame}{}
+\frametitle{Data}
 \includegraphics[scale=.5]{./sad-data/chapter2/bioregions.png}
@@
 \begin{frame}{}
+\frametitle{Data}
 \includegraphics[scale=.5]{./sad-data/chapter2/taxa_sites.png}
@@
 \begin{frame}{}
+\frametitle{Data}
 \includegraphics[scale=.5]{./sad-data/chapter2/num_taxa.png}
@@
 
+\subsection{Additional Data}
+
 \begin{frame}{}
+\frametitle{Data}
+\includegraphics[scale=.5]{./sad-data/chapter3/partial_sites_map.png}
+\end{frame}
+
+\section{Species abundance distribution comparisons}
+\subsection{Analysis}
+\subsection{Results}
+\begin{frame}{}
+\frametitle{Abundance distribution Comparisons}
 \includegraphics[scale=.5]{./sad-data/chapter1/AICc_weights.png}
@@
 \begin{frame}{}
+\frametitle{Abundance distribution Comparisons}
 \includegraphics[scale=.5]{./sad-data/chapter1/likelihoods.png}
@@
 \begin{frame}{}
+\frametitle{Abundance distribution Comparisons}
 \includegraphics[scale=.5]{./sad-data/chapter1/likelihoods_one_to_one.png}
@@
 
+\section{Neutral analysis}
+\subsection{Analysis}
+\subsection{Results}
 \begin{frame}{}
-\includegraphics[scale=.3]{./sad-data/chapter3/distabclasses_vs_lognormwgt.png}
+\frametitle{Neutral Analysis}
+\includegraphics[scale=.25]{./sad-data/chapter3/distabclasses_vs_lognormwgt.png}
 \end{frame}
 
+\begin{frame}{}
+\frametitle{Neutral Analysis}
+\includegraphics[scale=.6]{./sad-data/chapter3/avgvals_by_dataset.png}
+\end{frame}
+
+\section{Conclusions}
+
+\section{Acknowledgements}
+\subsection{Accessibility}
+
 \end{document}

### 2015-03-17 sad_neutral_analysis.py
Moves mapping code into function, makes two separate maps, a Mollweide projectionf for publication, and a Robinson for presentation.

@@ -120,39 +120,46 @@ plt.show()
 plt.close()
 
 #Mapping code modified from White et al. 2012
-"""Generate a world map with sites color-coded by database"""
-map = Basemap(projection='moll',lon_0=0,resolution='i') #Sets up map for Mollweide projection- chosen for equal area properties.
+def map_sites(projection, output_file):
+    """Generate a world map with sites color-coded by database"""
+    map = Basemap(projection=projection,lon_0=0,resolution='i') #Sets up map for Mollweide projection- chosen for equal area properties.
 
-map.drawcoastlines(linewidth = .10)
-map.fillcontinents(color='black',lake_color='white')
+    map.drawcoastlines(linewidth = .10)
+    map.fillcontinents(color='black',lake_color='white')
 
-datasets = ['bbs', 'cbc', 'fia', 'naba', 'mcdb', 'gentry' ] # The rest of the data do not have lat-longs.
-data_dir = './sad-data/chapter1/'
-markers=['o', '^', 's','D','v', 'p']
-markersizes=3
-colors=["teal", 'c', "seagreen", "m", "gold", 'palegreen']
+    datasets = ['bbs', 'cbc', 'fia', 'naba', 'mcdb', 'gentry' ] # The rest of the data do not have lat-longs.
+    data_dir = './sad-data/chapter1/'
+    markers=['o', '^', 's','D','v', 'p']
+    markersizes=3
+    colors=["teal", 'c', "seagreen", "m", "gold", 'palegreen']
 
 
-for i, dataset in enumerate(datasets):
-    latlong_data = import_latlong_data(data_dir + dataset + '_lat_long.csv')
-    lats = latlong_data["lat"]
-    longs = latlong_data["long"]
-    x,y = map(longs,lats)
-    map.plot(x,y, ls='', marker=markers[i], markeredgecolor= colors[i],
-    markeredgewidth=0.5, markersize=markersizes, fillstyle='none')
+    for i, dataset in enumerate(datasets):
+        latlong_data = import_latlong_data(data_dir + dataset + '_lat_long.csv')
+        lats = latlong_data["lat"]
+        longs = latlong_data["long"]
+        x,y = map(longs,lats)
+        map.plot(x,y, ls='', marker=markers[i], markeredgecolor= colors[i],
[…]

### 2015-03-19 defense_pres.tex
Tweaks size of map after fixing.
More presentation work- adds acknowledgements and intro.

@@
 
-\begin{frame}
+\begin{frame}[t]
 \titlepage
@@
 
+\section{Introduction}
+\subsection{What is macroecology?}
+\begin{frame}
+\frametitle{Macroecology}
+One approach to studying ecological patterns and processes.
+\begin{itemize}
+\item Data intensive.
+\item Large scales (spatial, temporal, taxonomic).
+\item Search for generality.
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Macroecology}
+Criticisms of macroecology
+\begin{itemize}
+\item North American terrestrial bias.
+\item Lack of identification of pattern generating mechanisms.
+\end{itemize}
+\end{frame}
+
 \section{Data}
-
 \subsection{Compiled Data}
@@
 \frametitle{Data}
-\includegraphics[scale=.5]{./sad-data/chapter3/partial_sites_map.png}
+\includegraphics[scale=.55]{./sad-data/chapter3/presentation_map.png}
 \end{frame}
@@
 \section{Acknowledgements}
+\begin{frame}[t]{}
+\frametitle{Acknowledgements}
+~\\ %Adds vertical space for better aesthetics
+\small{Funding sources:}
+\begin{tiny}
+\begin{itemize}
+\item USU Department of Biology
+\item Intellectual Ventures private funding to Morgan Ernest
+\item National Science Foundation CAREER Grant to Ethan White
+\item Gordon \& Betty Moore Foundation's Data-Driven Discovery Initiative Grant to Ethan White.
+\item USU Graduate School Dissertation Fellowship
+\end{itemize}
+\end{tiny}
+\end{frame}
+
+\begin{frame}{}
+\frametitle{Acknowledgements}
+The Weecologists
+\includegraphics[scale=.3]{../Miscellaneous/Pictures/Phd/whiteboard.png}
+\begin{tiny}
+(especially Xiao Xiao \& Ken Locey (creator of the whiteboard))
+\end{tiny}
+\end{frame}
+
 \subsection{Accessibility}
+\begin{frame}{}
 
+\end{frame}
 \end{document}

### 2015-03-19 defense_pres.tex
Figures out how to do a nested list.
Works more on intro/data section.

@@
-\documentclass[17pt]{beamer}
+\documentclass[14pt]{beamer}
 \usetheme{Pittsburgh}
@@
 \setbeamerfont{author}{size=\small}
-\setbeamerfont{frametitle}{size=\small}
+\setbeamerfont{frametitle}{size=\large}
+\setbeamertemplate{enumerate items}[default]
 \author{Elita Baldridge}
@@
 \subsection{What is macroecology?}
-\begin{frame}
+\begin{frame}[t]
 \frametitle{Macroecology}
-One approach to studying ecological patterns and processes.
+\normalsize One approach to studying ecological patterns and processes.\\
 \begin{itemize}
 \item Data intensive.
-\item Large scales (spatial, temporal, taxonomic).
+\item Large scales
+\begin{itemize}
+\item Spatial
+\item Temporal
+\item Taxonomic
+\end{itemize}
 \item Search for generality.
@@
 
-\begin{frame}
+\subsection{Criticisms of macroecology}
+\begin{frame}[t]
 \frametitle{Macroecology}
-Criticisms of macroecology
+Criticisms of macroecology\\
 \begin{itemize}
@@
 
+\subsection{Best practices}
+\begin{frame}[t]
+\frametitle{Macroecology}
+Best practice recommendations\\
+\begin{itemize}
+\begin{small}
+\item Test patterns with multiple taxonomic groups/ecosystems.  
+\item Simultaneous testing of competing models and model predictions with a consistent statistical approach.
+\end{small}
+\end{itemize}
+\end{frame}
+
 \section{Data}
+\subsection{Introduction to Ecoinformatics}
+\begin{frame}[t]
+\frametitle{The Rules of Ecoinformatics}
+\begin{Large}
+Garbage in, garbage out.\\
+\end{Large}
+\begin{itemize}
+\item All data are good, not all data are appropriate.
+\item Fit the data to the question.
+\end{itemize}
+\end{frame}
+
+\subsection{Current Data}
+\begin{frame}[t]
+\frametitle{Data}
+\vspace{-7pt}
+\includegraphics[scale=.55]{./sad-data/chapter3/presentation_map.png}
+\end{frame}
+
+\begin{frame}[t]{}
+\frametitle{Data}
+\begin{large}
+Major macroecological datasets\\
+\end{large}
+\begin{itemize}
+\item Largely terrestrial
+\item Largely North American
+\item Many publicly available, some not.
+\end{itemize}
+~\\
+~\\
+~\\
+~\\
+\begin{large}
+Lots of data in the literature.\\
+\end{large}
+\end{frame}
+
 \subsection{Compiled Data}
@@
 
-\subsection{Additional Data}
-
-\begin{frame}{}
-\frametitle{Data}
-\includegraphics[scale=.55]{./sad-data/chapter3/presentation_map.png}
+\section{Species abundance distribution}
+\begin{frame}[t]{}
+\frametitle{Commonness \& rarity}
+~\\
+\begin{large}
+The species abundance distribution:
+\end{large}
+\begin{itemize}
+\item Describes the distribution of commonness \& rarity of species.
+\item One of the most fundamental and ubiquitous patterns in ecology.
+\item Exhibits a hollow curve distribution.
+\begin{itemize}
+\item Many rare species.
+\item Few common species.
+~\\
+\end{itemize}
+\item Many forms of the species abundance distribution (SAD).
+\end{itemize}
 \end{frame}
@@
 \begin{frame}{}
-\frametitle{Abundance distribution Comparisons}
+\frametitle{SAD Comparisons}
 \includegraphics[scale=.5]{./sad-data/chapter1/AICc_weights.png}
@@
 \begin{frame}{}
-\frametitle{Abundance distribution Comparisons}
+\frametitle{SAD Comparisons}
 \includegraphics[scale=.5]{./sad-data/chapter1/likelihoods.png}
@@
 \begin{frame}{}
-\frametitle{Abundance distribution Comparisons}
+\frametitle{SAD Comparisons}
 \includegraphics[scale=.5]{./sad-data/chapter1/likelihoods_one_to_one.png}
@@
 \frametitle{Acknowledgements}
-The Weecologists
+Weecologists past, present, \& future\\
 \includegraphics[scale=.3]{../Miscellaneous/Pictures/Phd/whiteboard.png}
@@
 \subsection{Accessibility}
-\begin{frame}{}
-
+\begin{frame}[t]{}
+\frametitle{Acknowledgements}
+~\\ %Adds vertical space for better aesthetics
+Dr. Thomas Price \& USU Student Health Center
 \end{frame}

### 2015-03-19 defense_pres.tex
Adds data, fiddles with formatting, starts analysis?

@@
 
-\section{Species abundance distribution}
+\section{The species abundance distribution}
+\subsection{Pattern description}
 \begin{frame}[t]{}
@@
 
+\subsection{Forms of the distribution}
+\begin{frame}
+\frametitle{Forms of the SAD}
+\begin{large}
+Model classes:
+\end{large}
+\begin{itemize}
+\item Purely statistical
+\item Branching process
+\item Population dynamics
+\item Niche partitioning
+\item Maximum entropy
+\item Feasible set/combinatorics
+\end{itemize}
+\end{frame}
+
 \section{Species abundance distribution comparisons}
+\begin{frame}
+\frametitle{SAD Comparisons}
+\begin{large}
+Most comparisons of the different models:
+\end{large}
+\begin{itemize}
+\item Use only a small subset of available models (typically two).
+\item Focus on a single ecosystem or taxonomic group
+\item Fail to use the most appropriate statistical methods. 
+\end{itemize}
+\end{frame}
+
 \subsection{Analysis}
+\begin{frame}[shrink=10]
+\frametitle{SAD Comparisons}
+~\\
+~\\
+Selected five models from four classes for comparison.
+\begin{table}
+\begin{tabular}{l|l}
+ Model class & Form of the distribution\\ 
+\hline
+ Purely statistical & Logseries, Poisson lognormal\\
+ Branching process & Zipf \\
+ Population dynamics & Negative binomial\\
+ Niche partitioning & Geometric \\
+\end{tabular}
+~\\
+~\\
+~\\
+~\\
+\caption{After B.J. McGill et al. 2007. Species abundance distributions: moving beyond single prediction theories to integration within an ecological framework. Ecology letters 10: 995-1015.}
+\end{table}
+\end{frame}
+
+\begin{frame}[shrink=35]
+\frametitle{SAD Comparisons}
+\begin{center}
+\begin{table}
+\begin{tabular}{l|c|l|r}
+ Dataset &Dataset code &Availability &Total sites\\
+\hline
+ Breeding Bird Survey &BBS &Public &2769\\
+ Christmas Bird Count &CBC &Private &1999\\
+ Gentry's Forest Transects &Gentry &Public &10355\\
+ Forest Inventory Analysis &FIA	 &Public &220\\
+ Mammal Community Database &MCDB &Public &103\\
+ N. American Butterfly Count &NABA &Private &400\\
+ Actinopterygii, this dissertation	 &Actinopterygii &Public &161\\
+ Reptilia, this dissertation &Reptilia &Public &138\\
+ Amphibia, this dissertation &Amphibia &Public &43\\
+ Coleoptera, this dissertation &Coleoptera &Public &5\\
+ Arachnida, this dissertation &Arachnida &Public &25\\
+\end{tabular}
+\caption{Datasets used for species-abundance distribution comparisons.
+Datasets marked as Private were obtained through data requests to the providers resulting in Memorandums of Understanding governing data use.}
+\end{table}
+\end{center}
+\end{frame}
+
 \subsection{Results}

### 2015-03-19 defense_pres.tex
More bits on data and analysis.

@@
 
+\subsection{Data Availability}
+\begin{frame}[t]
+\frametitle{Data}
+~\\
+~\\
+The final community abundance database is publicly available and importable through the EcoData Retriever.\\ 
+(http://www.ecodataretriever.org/)
+\end{frame}
+
 \section{The species abundance distribution}
@@
 
-\subsection{Analysis}
+\subsection{Data & Analysis}
+\subsubsection{Model selection}
 \begin{frame}[shrink=10]
@@
 
+\subsubsection{Analysis}
+\begin{frame}
+\frametitle{SAD Comparisons}
+~\\
+Analysis:
+\begin{itemize}
+\item Model fitting with maximum likelihood estimation. 
+\item Likelihood based model selection to compare the fits of the different models.
+\item Model comparison with corrected Aikaike Information Criterion (AICc) weights.
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{SAD Comparisons}
+~\\
+Computational tools:
+\begin{itemize}
+\item Model fitting, log-likelihood, and AICc calculations performed with macroecotools Python package.\\
+\begin{small}
+(https://github.com/weecology/macroecotools)
+\end{small}
+\item All of the analysis code and the majority of the data is publicly available.
+\begin{small}
+(https://github.com/weecology/sad-comparison)
+\end{small}
+\end{itemize}
+\end{frame}
+
+\subsubsection{Data}
 \begin{frame}[shrink=35]

### 2015-03-19 defense_pres.tex
Acknowledgements and accessibility.

@@
 \section{Conclusions}
+\begin{frame}{}
+~\\ 
+\frametitle{Conclusions}\
+Challenging to infer process from species abundance distributions alone.
+~\\ 
+\begin{itemize}
+\item Multiple mechanisms proposed for each SAD formulation.
+\item Broad model categorization (i.e. neutral or non-neutral) may be more productive.
+\item May not be one single suite of processes that dominates.
+\end{itemize} 
+\end{frame}
+
+\begin{frame}[t]{}
+\frametitle{Conclusions}\
+~\\ 
+Challenges in identifying mechanism among datasets.
+~\\ 
+\begin{itemize}
+\item Biological vs. non-biological differences (spatial structuring, sampling intensity).
+\item Diverse data removes uncertainty about non-biological pattern generating mechanisms.
+\item Even with a great deal of data, identifying mechanism is still challenging.
+\end{itemize} 
+\end{frame}
+
+\begin{frame}[t]{}
+\frametitle{Conclusions}\
+~\\ 
+\begin{large}
+Predictive macroecology
+\end{large}
+~\\ 
+\begin{itemize}
+\item Traditional approach is pattern to process to prediction.
+\item May be possible to generate robust ecological predictions from general patterns.
+\item Process and prediction may be two separate research goals.
+\end{itemize} 
+\end{frame}
 
@@
 
-\subsection{Accessibility}
 \begin{frame}[t]{}
@@
 ~\\ %Adds vertical space for better aesthetics
-Dr. Thomas Price \& USU Student Health Center
+Dr. Thomas Price \& USU Student Health Center.\\
+~\\
+The Flint Hills of Kansas.\\
+~\\
+Tea, electric blankets, \& heating pads.\\
+~\\
+A very supportive husband \& family.\\
 \end{frame}
+
+\subsection{Accessibility}
+\begin{frame}[t]{}
+\frametitle{Accessibility}
+\begin{flushright}
+This dissertation brought to you by:
+\end{flushright}
+\begin{Large}
+Disability accommodations\\
+\end{Large}
+~\\
+\begin{itemize}
+\item Remote access \& participation.\\
+\item Computational tools \& tricks.
+\begin{itemize}
+\item Version control (GitHub).
+\item Publicly available data.
+\item Programming skills (data manipulation \& analysis).
+\end{itemize}
+\end{itemize}
+\end{frame}
+
 \end{document}

### 2015-03-20 defense_pres.tex
More work on presentation.
Fleshes out the rest of everything.

@@
 
+\subsection{Conclusions}
+\begin{frame}
+\frametitle{SAD Comparisons}
+Existing models provide equivalently good absolute fits to empirical data.
+\begin{itemize}
+\item Models with fewer parameters perform better in AIC-based model selection.\\
+\item Logseries provides a good naive model for fitting SADs.\\
+\begin{itemize}
+\item Produces equivalent likelihoods.
+\item Has a single fitted parameter.
+\item Easy to fit to empirical data.
+\item Best overall model.
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{SAD Comparisons}
+Identifying pattern generating mechanisms:
+\begin{itemize}
+\item Compare predictions of different models using multiple macroecological patterns simultaneously.\\
+\item Examine scale dependence of pattern.
+\end{itemize}
+~\\
+~\\
+However, identification of mechanism may not be necessary for prediction.
+\end{frame}
+
 \section{Neutral analysis}
-\subsection{Analysis}
+\begin{frame}[t]
+\frametitle{Neutral Analysis}
+~\\
+The unified neutral theory of biodiversity:\\
+~\\
+\begin{itemize}
+\item Multiple formulations.
+\begin{itemize}
+\item Species and individuals are ecologically and demographically equivalent.\\
+\item Stochastic variation in birth, death, immigration, \& speciation results in species abundance differences.
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Neutral Analysis}
+Early tests of neutral theory based on comparing the fit of empirical species abundance distributions to the neutral prediction.\\
+~\\
+Later tests suggested species abundance comparisons were insufficient for a rigorous test of neutrality.\\
+~\\
+\end{frame}
+
+\begin{frame}
+\frametitle{Neutral Analysis}
+Connolly et al. 2014 identified non-neutral species abundance distributions in marine communities.\\
+\begin{small}
+\begin{itemize}
+\item Compared model fits of a non-neutral distribution (Poisson lognormal) to a neutral distribution (negative binomial distribution).\\
+\end{itemize}
+\end{small}
+~\\
+May be a robust method for identifying communities that exhibit non-neutrality.\\
+\begin{tiny}
+S.R. Connolly et al. 2014. Commonness and rarity in the marine biosphere. PNAS 111: 8524-8529.
+\end{tiny}
+\end{frame}
+
+\subsection{Data & Analysis}
+\begin{frame}
+\frametitle{Neutral Analysis}
+Used the same data and model fitting approach.\\
+Compared a non-neutral model (Poisson lognormal) to a neutral model (negative binomial).\\
+\end{frame}
+
 \subsection{Results}
@@
 
-\section{Conclusions}
+\subsection{Conclusions}
+\begin{frame}
+\frametitle{Neutral analysis}
+Difficult to identify a clear winning model.
+\begin{itemize}
+\item Results consistent with our species abundance distribution model comparisons. 
+\item Results different from Connolly et al. 2014.
+\begin{itemize}
+\item Non-neutral model outperforms the neutral model in marine systems.
+\item Our results suggest marine systems more generally approximated by non-neutral dynamics; terrestrial systems more variable between neutral and non-neutral dynamics.
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\section{General Conclusions}
 \begin{frame}{}

### 2015-03-22 defense_pres.tex
Tweaks formatting.
Typo.
Adds shiny, shiny illustrations because I have no fieldwork pictures.

@@
 \item Data intensive.
-\item Large scales
+\item Large scales.
 \begin{itemize}
@@
 \subsubsection{Data Summary}
+\begin{frame}{}
+\frametitle{Data}
+\includegraphics[scale=.4]{../Miscellaneous/Pictures/Phd/CompiledData.png}
+\end{frame}
+
 \begin{frame}{}
@@
 \end{center}
+\end{frame}
+
+\begin{frame}{}
+\frametitle{Data}
+\includegraphics[scale=.4]{../Miscellaneous/Pictures/Phd/MapCreatures.png}
 \end{frame}
@@
 \small{Funding sources:}
-\begin{tiny}
+\begin{small}
 \begin{itemize}
 \item USU Department of Biology
-\item Intellectual Ventures private funding to Morgan Ernest
+\item Intellectual Ventures, private funding to Morgan Ernest
 \item National Science Foundation CAREER Grant to Ethan White
@@
 \end{itemize}
-\end{tiny}
+\end{small}
 \end{frame}
@@
 \frametitle{Accessibility}
-\begin{flushright}
+\begin{center}
 This dissertation brought to you by:
-\end{flushright}
+\end{center}
 \begin{Large}

### 2015-03-23 sad_neutral_analysis.py
Keep functions grouped together

@@ -68,6 +68,47 @@ def get_pln_aicc_wgts(sads):
     negbin_rel_lik = np.exp(-(negbin_delta_aicc) / 2)
     return pln_rel_lik / (pln_rel_lik + negbin_rel_lik)
 
+#Mapping code modified from White et al. 2012
+def map_sites(projection, output_file):
+    """Generate a world map with sites color-coded by database"""
+    map = Basemap(projection=projection,lon_0=0,resolution='i') #Sets up map for Mollweide projection- chosen for equal area properties.
+
+    map.drawcoastlines(linewidth = .10)
+    map.fillcontinents(color='black',lake_color='white')
+
+    datasets = ['bbs', 'cbc', 'fia', 'naba', 'mcdb', 'gentry' ] # The rest of the data do not have lat-longs.
+    data_dir = './sad-data/chapter1/'
+    markers=['o', '^', 's','D','v', 'p']
+    markersizes=3
+    colors=["teal", 'c', "seagreen", "m", "gold", 'palegreen']
+
+
+    for i, dataset in enumerate(datasets):
+        latlong_data = import_latlong_data(data_dir + dataset + '_lat_long.csv')
+        lats = latlong_data["lat"]
+        longs = latlong_data["long"]
+        x,y = map(longs,lats)
+        map.plot(x,y, ls='', marker=markers[i], markeredgecolor= colors[i],
+        markeredgewidth=0.5, markersize=markersizes, fillstyle='none')
+
+
+    #Make legend
+    l1 = plt.scatter([],[], s=60, marker = 'o', facecolors='teal',  edgecolors='black')
+    l2 = plt.scatter([],[], s=60, marker = '^', facecolors='c', edgecolors='black')
+    l3 = plt.scatter([],[], s=60, marker = 's', facecolors='seagreen', edgecolors='black')
+    l4 = plt.scatter([],[], s=60, marker = 'D', facecolors='m', edgecolors='black')
+    l5 = plt.scatter([],[], s=60, marker = 'v', facecolors='gold', edgecolors='black')
+    l6 = plt.scatter([],[], s=60, marker = 'p', facecolors='palegreen', edgecolors='black')
+
+    labels = ["BBS", "CBC", "FIA", "NABA", "MCDB", "Gentry"]
+
+    leg = plt.legend([l1, l2, l3, l4, l5, l6], labels, frameon=False, fontsize=8, loc = 6, scatterpoints = 1)
+
+    plt.tight_layout()
+
[…]

### 2015-03-23 sad_neutral_analysis.py
Minor whitespace cleanup

@@ -147,7 +147,6 @@ ax.savefig('./sad-data/chapter3/distabclasses_vs_lognormwgt.png')
 plt.close()
 
 # Create figure showing average values for each datasets
-
 sads_by_dataset = sads.groupby('dataset').mean().reset_index()
 ax = sns.lmplot('log_distinct_ab_vals', 'pln_aicc_wgt', data=sads_by_dataset,
                 hue='dataset', fit_reg=False, scatter_kws={"s": 60, "alpha": 1})
@@ -160,7 +159,6 @@ ax.savefig('./sad-data/chapter3/avgvals_by_dataset.png')
 plt.show()
 plt.close()
 
-
+# Create map of sites
 map_sites('moll', './sad-data/chapter3/partial_sites_map.png') #Mollweide projection, for publication
-
 map_sites('robin', './sad-data/chapter3/presentation_map.png') #Robinson projection, for presentation

### 2015-03-23 sad_neutral_analysis.py
Add functional for making histograms with empirical data and models

@@ -4,6 +4,8 @@ Conducts analyses in Connolly et al. 2014 (in PNAS) using ~17,000 empirical SADS
 
 """
 
+from __future__ import division
+
 import os
 import glob
 import functools
@@ -16,7 +18,8 @@ import seaborn as sns
 from mpl_toolkits.axes_grid.inset_locator import inset_axes
 from mpl_toolkits.basemap import Basemap
 
-from macroecotools import AICc, aic_weight
+from macroecotools import AICc, aic_weight, preston_sad, hist_pmf
+from macroeco_distributions import pln, nbinom_lower_trunc
 from sad_comparison_functions import get_par_multi_dists, get_loglik_multi_dists
 
 def get_dataset_name(pathname):
@@ -67,6 +70,26 @@ def get_pln_aicc_wgts(sads):
     pln_rel_lik = np.exp(-(pln_delta_aicc) / 2)
     negbin_rel_lik = np.exp(-(negbin_delta_aicc) / 2)
     return pln_rel_lik / (pln_rel_lik + negbin_rel_lik)
+
+def make_hist_empir_model(abunds):
+    """Make a histogram comparing the two models to the empirical data"""
+    xs = range(1, max(abunds) * 2)
+    pln_paras = get_par_multi_dists(abunds, 'pln') + (1,) #add truncation at 1
+    negbin_paras = get_par_multi_dists(abunds, 'negbin')
+    pln_pmf = pln.pmf(xs, *pln_paras)
+    negbin_pmf = nbinom_lower_trunc.pmf(xs, *negbin_paras)
+    hist_empir, hist_bins = preston_sad(abunds)
+    hist_empir = hist_empir / sum(hist_empir)
+    hist_pln, _ = hist_pmf(xs, pln_pmf, hist_bins)
+    hist_negbin, _ = hist_pmf(xs, negbin_pmf, hist_bins)
+    hist_bins_log = np.log2(hist_bins)
+    xticks = hist_bins_log[:-1] + 0.5
+    xvalues =  [int(np.exp2(val)) for val in hist_bins_log[:-1]]
+    plt.bar(hist_bins_log[:-1], hist_empir, color='gray', width=1)
+    plt.plot(xticks, hist_pln, linewidth=4)
+    plt.plot(xticks, hist_negbin, linewidth=4)
+    plt.xticks(xticks, xvalues)
+    plt.show()
 
 #Mapping code modified from White et al. 2012
 def map_sites(projection, output_file):

### 2015-03-23 sad_neutral_analysis.py
Works on adding graphs for empirical vs. model histograms.

@@ -71,7 +71,7 @@ def get_pln_aicc_wgts(sads):
     negbin_rel_lik = np.exp(-(negbin_delta_aicc) / 2)
     return pln_rel_lik / (pln_rel_lik + negbin_rel_lik)
 
-def make_hist_empir_model(abunds):
+def make_hist_empir_model(abunds, output_file):
     """Make a histogram comparing the two models to the empirical data"""
     xs = range(1, max(abunds) * 2)
     pln_paras = get_par_multi_dists(abunds, 'pln') + (1,) #add truncation at 1
@@ -89,7 +89,13 @@ def make_hist_empir_model(abunds):
     plt.plot(xticks, hist_pln, linewidth=4)
     plt.plot(xticks, hist_negbin, linewidth=4)
     plt.xticks(xticks, xvalues)
+    
+    plt.tight_layout()
+
+    plt.savefig(output_file, dpi=250)
     plt.show()
+    plt.close()    
+
 
 #Mapping code modified from White et al. 2012
 def map_sites(projection, output_file):
@@ -185,3 +191,25 @@ plt.close()
 # Create map of sites
 map_sites('moll', './sad-data/chapter3/partial_sites_map.png') #Mollweide projection, for publication
 map_sites('robin', './sad-data/chapter3/presentation_map.png') #Robinson projection, for presentation
+
+#Create histograms of empirical vs. model SADs
+datasets = ['Actinopterygii', 'Amphibia', 'Arachnida', 'bbs', 'cbc', 'Coleoptera',
+                'fia', 'gentry', 'mcdb', 'naba', 'Reptilia']
+
+for dataset in datasets:
+    raw_data = import_data(dataset, './sad-data/chapter3/')
+    
+    usites = np.sort(list(set(raw_data["site"])))
+
+    for i,site in enumerate(sites):
+        if i == 0:
+            subsites = raw_data["site"][raw_data["site"] == site] 
+            subabundance = raw_data["ab"][raw_data["site"] == site]
+            output_file = './sad-data/chapter3/EmpirModelHist_' + dataset + '.png'
+            make_hist_empir_model(abunds, output_file)
+            
+        else:
+            break
+    
+    
+        

### 2015-03-23 sad_neutral_analysis.py
Still working on adding graphs.

@@ -44,6 +44,11 @@ def import_data(datasets, datadir):
         data = data.append(new_data, ignore_index=True)
     return data
 
+def import_abundance(datafile):
+    """Imports raw species abundance .csv files in the form: Site, Year, Species, Abundance."""
+    raw_data = np.genfromtxt(datafile, dtype = "S15,i8,S50,i8", names = ['site','year','sp','ab'], delimiter = ",",comments = "#")
+    return raw_data
+
 def import_latlong_data(input_filename, comments='#'):
     data = np.genfromtxt(input_filename, dtype = "f8,f8",
                          names = ['lat','long'], delimiter = ",")
@@ -196,16 +201,19 @@ map_sites('robin', './sad-data/chapter3/presentation_map.png') #Robinson project
 datasets = ['Actinopterygii', 'Amphibia', 'Arachnida', 'bbs', 'cbc', 'Coleoptera',
                 'fia', 'gentry', 'mcdb', 'naba', 'Reptilia']
 
-for dataset in datasets:
-    raw_data = import_data(dataset, './sad-data/chapter3/')
-    
-    usites = np.sort(list(set(raw_data["site"])))
+analysis_ext = '_spab.csv'
+data_dir = './sad-data/chapter3/EmpirModelHist_'
+fig_ext = '_EmpirModelHist.png'
 
+for dataset in datasets:
+    datafile = datafile = data_dir + dataset + analysis_ext
+    raw_data = import_abundance(datafile)
     for i,site in enumerate(sites):
+        usites = np.sort(list(set(raw_data["site"])))
         if i == 0:
             subsites = raw_data["site"][raw_data["site"] == site] 
             subabundance = raw_data["ab"][raw_data["site"] == site]
-            output_file = './sad-data/chapter3/EmpirModelHist_' + dataset + '.png'
+            output_file = data_dir + dataset + fig_ext
             make_hist_empir_model(abunds, output_file)
             
         else:

### 2015-03-23 sad_neutral_analysis.py
Typo.

@@ -202,7 +202,7 @@ datasets = ['Actinopterygii', 'Amphibia', 'Arachnida', 'bbs', 'cbc', 'Coleoptera
                 'fia', 'gentry', 'mcdb', 'naba', 'Reptilia']
 
 analysis_ext = '_spab.csv'
-data_dir = './sad-data/chapter3/EmpirModelHist_'
+data_dir = './sad-data/chapter3/'
 fig_ext = '_EmpirModelHist.png'
 
 for dataset in datasets:

### 2015-03-23 sad_neutral_analysis.py
Working graphs.

@@ -208,16 +208,14 @@ fig_ext = '_EmpirModelHist.png'
 for dataset in datasets:
     datafile = datafile = data_dir + dataset + analysis_ext
     raw_data = import_abundance(datafile)
-    for i,site in enumerate(sites):
-        usites = np.sort(list(set(raw_data["site"])))
-        if i == 0:
-            subsites = raw_data["site"][raw_data["site"] == site] 
-            subabundance = raw_data["ab"][raw_data["site"] == site]
-            output_file = data_dir + dataset + fig_ext
-            make_hist_empir_model(abunds, output_file)
-            
-        else:
-            break
-    
-    
+    usites = np.sort(list(set(raw_data["site"])))
+    for site in usites:
+        subsites = raw_data["site"][raw_data["site"] == site]        
+        subabundance = raw_data["ab"][raw_data["site"] == site]
         
+        N = sum(subabundance) # N = total abundance for a site
+        S = len(subsites) # S = species richness at a site
+        if S > 10:        
+            output_file = data_dir + dataset + fig_ext
+            make_hist_empir_model(subabundance, output_file)  
+            break

### 2015-03-23 sad_neutral_analysis.py
Uses first site where N > 15, tries to add figure legend.

@@ -91,9 +91,11 @@ def make_hist_empir_model(abunds, output_file):
     xticks = hist_bins_log[:-1] + 0.5
     xvalues =  [int(np.exp2(val)) for val in hist_bins_log[:-1]]
     plt.bar(hist_bins_log[:-1], hist_empir, color='gray', width=1)
-    plt.plot(xticks, hist_pln, linewidth=4)
-    plt.plot(xticks, hist_negbin, linewidth=4)
+    pln_line = plt.plot(xticks, hist_pln, linewidth=4, color = 'm', label='Poisson lognormal')
+    negbin_line = plt.plot(xticks, hist_negbin, linewidth=4, color = 'c', label='Negative binomial')
     plt.xticks(xticks, xvalues)
+    
+    plt.legend(handles=[pln_line, negbin_line])
     
     plt.tight_layout()
 
@@ -215,7 +217,7 @@ for dataset in datasets:
         
         N = sum(subabundance) # N = total abundance for a site
         S = len(subsites) # S = species richness at a site
-        if S > 10:        
+        if S > 15:        
             output_file = data_dir + dataset + fig_ext
             make_hist_empir_model(subabundance, output_file)  
             break

### 2015-03-23 sad_neutral_analysis.py
Adds legend.

@@ -91,11 +91,18 @@ def make_hist_empir_model(abunds, output_file):
     xticks = hist_bins_log[:-1] + 0.5
     xvalues =  [int(np.exp2(val)) for val in hist_bins_log[:-1]]
     plt.bar(hist_bins_log[:-1], hist_empir, color='gray', width=1)
-    pln_line = plt.plot(xticks, hist_pln, linewidth=4, color = 'm', label='Poisson lognormal')
-    negbin_line = plt.plot(xticks, hist_negbin, linewidth=4, color = 'c', label='Negative binomial')
+    plt.plot(xticks, hist_pln, linewidth=4, color = 'm')
+    plt.plot(xticks, hist_negbin, linewidth=4, color = 'c')
+       
     plt.xticks(xticks, xvalues)
     
-    plt.legend(handles=[pln_line, negbin_line])
+    pln_line = plt.scatter([],[], s=60, marker = 's', facecolors='m', edgecolors='black')
+    negbin_line = plt.scatter([],[], s=60, marker = 's', facecolors='c', edgecolors='black')    
+    
+    labels = ["Poisson lognormal", "Negative binomial"]
+
+ for l   plt.legend([pln_line, negbin_line], labels, frameon=False, fontsize=12, scatterpoints = 1)
+
     
     plt.tight_layout()
 

### 2015-03-23 sad_neutral_analysis.py
Changes legend to include dataset.

@@ -76,7 +76,7 @@ def get_pln_aicc_wgts(sads):
     negbin_rel_lik = np.exp(-(negbin_delta_aicc) / 2)
     return pln_rel_lik / (pln_rel_lik + negbin_rel_lik)
 
-def make_hist_empir_model(abunds, output_file):
+def make_hist_empir_model(abunds, dataset, output_file):
     """Make a histogram comparing the two models to the empirical data"""
     xs = range(1, max(abunds) * 2)
     pln_paras = get_par_multi_dists(abunds, 'pln') + (1,) #add truncation at 1
@@ -101,9 +101,8 @@ def make_hist_empir_model(abunds, output_file):
     
     labels = ["Poisson lognormal", "Negative binomial"]
 
- for l   plt.legend([pln_line, negbin_line], labels, frameon=False, fontsize=12, scatterpoints = 1)
-
-    
+    plt.legend([pln_line, negbin_line], labels, frameon=False, fontsize=12, scatterpoints = 1, title = dataset)
+        
     plt.tight_layout()
 
     plt.savefig(output_file, dpi=250)
@@ -226,5 +225,5 @@ for dataset in datasets:
         S = len(subsites) # S = species richness at a site
         if S > 15:        
             output_file = data_dir + dataset + fig_ext
-            make_hist_empir_model(subabundance, output_file)  
+            make_hist_empir_model(subabundance, dataset, output_file)  
             break

### 2015-03-23 sad_neutral_analysis.py
Makes single figure with subplots for each dataset.

@@ -76,36 +76,62 @@ def get_pln_aicc_wgts(sads):
     negbin_rel_lik = np.exp(-(negbin_delta_aicc) / 2)
     return pln_rel_lik / (pln_rel_lik + negbin_rel_lik)
 
-def make_hist_empir_model(abunds, dataset, output_file):
-    """Make a histogram comparing the two models to the empirical data"""
-    xs = range(1, max(abunds) * 2)
-    pln_paras = get_par_multi_dists(abunds, 'pln') + (1,) #add truncation at 1
-    negbin_paras = get_par_multi_dists(abunds, 'negbin')
-    pln_pmf = pln.pmf(xs, *pln_paras)
-    negbin_pmf = nbinom_lower_trunc.pmf(xs, *negbin_paras)
-    hist_empir, hist_bins = preston_sad(abunds)
-    hist_empir = hist_empir / sum(hist_empir)
-    hist_pln, _ = hist_pmf(xs, pln_pmf, hist_bins)
-    hist_negbin, _ = hist_pmf(xs, negbin_pmf, hist_bins)
-    hist_bins_log = np.log2(hist_bins)
-    xticks = hist_bins_log[:-1] + 0.5
-    xvalues =  [int(np.exp2(val)) for val in hist_bins_log[:-1]]
-    plt.bar(hist_bins_log[:-1], hist_empir, color='gray', width=1)
-    plt.plot(xticks, hist_pln, linewidth=4, color = 'm')
-    plt.plot(xticks, hist_negbin, linewidth=4, color = 'c')
-       
-    plt.xticks(xticks, xvalues)
-    
-    pln_line = plt.scatter([],[], s=60, marker = 's', facecolors='m', edgecolors='black')
-    negbin_line = plt.scatter([],[], s=60, marker = 's', facecolors='c', edgecolors='black')    
-    
-    labels = ["Poisson lognormal", "Negative binomial"]
-
-    plt.legend([pln_line, negbin_line], labels, frameon=False, fontsize=12, scatterpoints = 1, title = dataset)
+def make_hist_empir_model(datasets, analysis_ext, data_dir, fig_ext):
+    plt.figure()
+    for i, dataset in enumerate (datasets):
+        datafile = datafile = data_dir + dataset + analysis_ext
+        raw_data = import_abundance(datafile)
+        usites = np.sort(list(set(raw_data["site"])))
+        subplot = i + 1
+        ax  = plt.subplot(4,3, subplot)    
         
-    plt.tight_layout()
[…]

### 2015-03-23 sad_neutral_analysis.py
Noticed x-tick labels run over each other, rotation.

@@ -111,13 +111,10 @@ def make_hist_empir_model(datasets, analysis_ext, data_dir, fig_ext):
                 plt.plot(xticks, hist_pln, linewidth=2, color = 'm')
                 plt.plot(xticks, hist_negbin, linewidth=2, color = 'c')
                     
-                plt.xticks(xticks, xvalues)
+                plt.xticks(xticks, xvalues,  rotation=17)
                 plt.title(dataset)                
 
                 plt.tight_layout()
-            
-                               
-                
     
                 break   
             

### 2015-03-23 sad_neutral_analysis.py
Fixes tick labels.

@@ -111,7 +111,8 @@ def make_hist_empir_model(datasets, analysis_ext, data_dir, fig_ext):
                 plt.plot(xticks, hist_pln, linewidth=2, color = 'm')
                 plt.plot(xticks, hist_negbin, linewidth=2, color = 'c')
                     
-                plt.xticks(xticks, xvalues,  rotation=17)
+                plt.xticks(xticks, xvalues,  rotation='vertical', fontsize = 'x-small')
+                plt.yticks(fontsize = 'x-small')
                 plt.title(dataset)                
 
                 plt.tight_layout()

### 2015-03-23 sad_neutral_analysis.py
Shrinks dataset name.

@@ -113,7 +113,7 @@ def make_hist_empir_model(datasets, analysis_ext, data_dir, fig_ext):
                     
                 plt.xticks(xticks, xvalues,  rotation='vertical', fontsize = 'x-small')
                 plt.yticks(fontsize = 'x-small')
-                plt.title(dataset)                
+                plt.title(dataset, fontsize = 'small')               
 
                 plt.tight_layout()
     

### 2015-03-26 defense_pres.tex
Modifies presentation graphs for greater crowd appeal.

@@
 \frametitle{Data}
-\includegraphics[scale=.4]{../Miscellaneous/Pictures/Phd/CompiledData.png}
+\includegraphics[scale=.35]{../Miscellaneous/Pictures/Phd/CompiledData.png}
 \end{frame}
@@
 \frametitle{Data}
-\includegraphics[scale=.5]{./sad-data/chapter2/bioregions.png}
+\includegraphics[scale=.5]{./sad-data/dissertation/bioregions.png}
 \end{frame}
@@
 \frametitle{Data}
-\includegraphics[scale=.5]{./sad-data/chapter2/taxa_sites.png}
+\includegraphics[scale=.45]{./sad-data/dissertation/taxa_sites.png}
 \end{frame}
@@
 \frametitle{Data}
-\includegraphics[scale=.5]{./sad-data/chapter2/num_taxa.png}
+\includegraphics[scale=.45]{./sad-data/dissertation/num_taxa.png}
 \end{frame}
@@
 \frametitle{SAD Comparisons}
-\includegraphics[scale=.5]{./sad-data/chapter1/AICc_weights.png}
+\includegraphics[scale=.5]{./sad-data/dissertation/AICc_weights.png}
 \end{frame}
@@
 \frametitle{SAD Comparisons}
-\includegraphics[scale=.5]{./sad-data/chapter1/likelihoods.png}
+\includegraphics[scale=.5]{./sad-data/dissertation/likelihoods.png}
 \end{frame}
@@
 \frametitle{SAD Comparisons}
-\includegraphics[scale=.5]{./sad-data/chapter1/likelihoods_one_to_one.png}
+\includegraphics[scale=.5]{./sad-data/dissertation/likelihoods_one_to_one.png}
 \end{frame}
@@
 
+\begin{frame}{}
+\frametitle{Neutral Analysis}
+\includegraphics[scale=.43]{./sad-data/dissertation/EmpirModelHist.png}
+\end{frame}
+
 \subsection{Results}
@@
 \frametitle{Neutral Analysis}
-\includegraphics[scale=.25]{./sad-data/chapter3/distabclasses_vs_lognormwgt.png}
+\includegraphics[scale=.45]{./sad-data/dissertation/distabclasses_vs_lognormwgt.png}
 \end{frame}
@@
 \frametitle{Neutral Analysis}
-\includegraphics[scale=.6]{./sad-data/chapter3/avgvals_by_dataset.png}
+\includegraphics[scale=.40]{./sad-data/dissertation/avgvals_by_dataset.png}
 \end{frame}

### 2015-03-28 defense_pres.tex
Changes something minor.
Adds some additional graphs, section on signal and noise.

@@
 
+\section{Title}
 \begin{frame}[t]
@@
 
+\subsection{Signal and Noise}
+\begin{frame}[t]
+\frametitle{Signal \& Noise}
+\begin{center}
+\includegraphics[scale=.05]{../Miscellaneous/Pictures/Maps/TheMapsCoarse.png}
+\end{center}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Signal \& Noise}
+\begin{center}
+\includegraphics[scale=.05]{../Miscellaneous/Pictures/Maps/TheMapsMiddle.png}
+\end{center}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Signal \& Noise}
+\begin{center}
+\includegraphics[scale=.2]{../Miscellaneous/Pictures/Maps/TheMaps.png}
+\end{center}
+\end{frame}
+
 \subsection{Criticisms of macroecology}
@@
 
-\section{Data}
 \subsection{Introduction to Ecoinformatics}
@@
 
+\section{Data}
 \subsection{Current Data}
@@
 \subsection{Compiled Data}
+\begin{frame}{}
+\frametitle{Data}
+\includegraphics[scale=.35]{../Miscellaneous/Pictures/Phd/CompiledData.png}
+\end{frame}
+
 \subsubsection{Data Collection}
@@
 \subsubsection{Data Summary}
-\begin{frame}{}
-\frametitle{Data}
-\includegraphics[scale=.35]{../Miscellaneous/Pictures/Phd/CompiledData.png}
-\end{frame}
-
 \begin{frame}{}
@@
 \subsection{Results}
+\begin{frame}{}
+\frametitle{SAD Comparisons}
+\includegraphics[scale=.5]{./sad-data/dissertation/total_wins.png}
+\end{frame}
+
+\begin{frame}{}
+\frametitle{SAD Comparisons}
+\includegraphics[scale=.40]{./sad-data/dissertation/wins_by_dataset.png}
+\end{frame}
+
 \begin{frame}{}
@@
 
+\section{Finis}
+\begin{frame}[t]
+\frametitle{Questions?}
+\begin{center}
+\includegraphics[scale=.2]{../Miscellaneous/Pictures/Maps/TheMaps.png}
+\end{center}
+\end{frame}
+
 \end{document}

### 2015-03-28 defense_pres.tex
Adds pattern process prediction slide.
Uses smaller pictures.

@@
 \usepackage{graphicx}
+\usepackage{marvosym}
 \usefonttheme{structuresmallcapsserif}
@@
 
+\begin{frame}
+\frametitle{Macroecology}
+\begin{Huge}
+\begin{center}
+
+Pattern
+
+\MVArrowDown{}
+
+Process
+
+\MVArrowDown{}
+
+Prediction
+
+\end{center}
+\end{Huge}
+\end{frame}
+
 \subsection{Signal and Noise}
@@
 \begin{center}
-\includegraphics[scale=.05]{../Miscellaneous/Pictures/Maps/TheMapsCoarse.png}
+\includegraphics[scale=.28]{../Miscellaneous/Pictures/Maps/TheMapsCoarse.jpg}
 \end{center}
@@
 \begin{center}
-\includegraphics[scale=.05]{../Miscellaneous/Pictures/Maps/TheMapsMiddle.png}
+\includegraphics[scale=.28]{../Miscellaneous/Pictures/Maps/TheMapsMiddle.jpg}
 \end{center}
@@
 \begin{center}
-\includegraphics[scale=.2]{../Miscellaneous/Pictures/Maps/TheMaps.png}
+\includegraphics[scale=.28]{../Miscellaneous/Pictures/Maps/TheMaps.jpg}
 \end{center}

### 2015-04-01 defense_pres.tex
Expands introduction, simplifies signal and noise slides.

@@
 \section{Introduction}
+\subsection{Commonness & rarity}
+\begin{frame}[t]
+\frametitle{Commonness \& rarity}
+"Who can explain why one species ranges widely, and is very numerous, and why another allied species has a narrow range and is rare?
+Yet these relations are of the highest important, for they determine the present welfare and, as I believe, the future success and modification of every inhabitant of this world."
+
+Darwin, 1859.
+
+\note{
+Few common species.
+Many rare species.
+One of the most fundamental and ubiquitous patterns in ecology.}
+\end{frame}
+
+\begin{frame}
+Species abundance distribution
+\begin{itemize}
+\item Describes the distribution of commonness \& rarity of species.
+\item Exhibits a hollow curve distribution.
+\end{itemize}
+\note{
+Relative abundance distribution (RAD)
+Species abundance distribution (SAD)}
+\end{frame}
+
 \subsection{What is macroecology?}
@@
 
+\subsection{Challenges of macroecology}
+\begin{frame}[t]
+\frametitle{Macroecology}
+Challenges of macroecology\\
+\begin{itemize}
+\item Studies performed with a limited number of large datasets.
+\item Lack of identification of pattern generating mechanisms.
+\end{itemize}
+\note{
+Taxonomic and ecosystem limitations in datasets, e.g.North American terrestrial bias.}
+\end{frame}
+
 \subsection{Signal and Noise}
@@
 \begin{center}
-\includegraphics[scale=.28]{../Miscellaneous/Pictures/Maps/TheMapsCoarse.jpg}
+\includegraphics[scale=.4]{./sad-data/chapter3/SignalNoise.png}
 \end{center}
-\end{frame}
-
-\begin{frame}[t]
-\frametitle{Signal \& Noise}
-\begin{center}
-\includegraphics[scale=.28]{../Miscellaneous/Pictures/Maps/TheMapsMiddle.jpg}
-\end{center}
-\end{frame}
-
-\begin{frame}[t]
-\frametitle{Signal \& Noise}
-\begin{center}
-\includegraphics[scale=.28]{../Miscellaneous/Pictures/Maps/TheMaps.jpg}
-\end{center}
-\end{frame}
-
-\subsection{Criticisms of macroecology}
-\begin{frame}[t]
-\frametitle{Macroecology}
-Criticisms of macroecology\\
-\begin{itemize}
-\item North American terrestrial bias.
-\item Lack of identification of pattern generating mechanisms.
-\end{itemize}
 \end{frame}

### 2015-04-01 defense_pres.tex
Adds inclusion criteria slide.

@@
 \begin{center}
-\includegraphics[scale=.4]{./sad-data/chapter3/SignalNoise.png}
+\includegraphics[scale=.4]{./sad-data/dissertation/SignalNoise.png}
 \end{center}
@@
 \subsubsection{Data Collection}
+\subsection{Compiled Data}
+\begin{frame}[t]{}
+\frametitle{Data}
+Inclusion criteria:
+\begin{itemize}
+\item Quantitative abundances
+\item Animals
+\item Complete sampling
+\item Must not be heavily summarized or processed
+\item High degree of taxonomic resolution
+\item Observational
+\end{itemize}
+\end{frame}
+
 \begin{frame}[shrink=30]
@@
 ~\\
-\caption{After B.J. McGill et al. 2007. Species abundance distributions: moving beyond single prediction theories to integration within an ecological framework. Ecology letters 10: 995-1015.}
+\caption{After B.J. McGill et al. 2007.}
 \end{table}
@@
 \begin{tiny}
-S.R. Connolly et al. 2014. Commonness and rarity in the marine biosphere. PNAS 111: 8524-8529.
+Connolly et al. 2014.
 \end{tiny}
@@
 Compared a non-neutral model (Poisson lognormal) to a neutral model (negative binomial).\\
+\end{frame}
+
+\begin{frame}{}
+\frametitle{Neutral Analysis}
+\includegraphics[scale=.43]{./sad-data/dissertation/Connolly2014AB.png}
+\begin{tiny}
+Connolly et al. 2014.
+\end{tiny}
 \end{frame}

### 2015-04-02 defense_pres.tex

@@
 \subsubsection{Data Collection}
-\subsection{Compiled Data}
 \begin{frame}[t]{}
@@
 \end{itemize}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Data wrangling}
+\begin{center}
+\includegraphics[scale=.27]{./sad-data/dissertation/Wrangling.png}
+\end{center}
+\begin{tiny}
+Cavitt 2000.
+\end{tiny}
 \end{frame}
@@
 \subsection{Data Availability}
-\begin{frame}[t]
-\frametitle{Data}
+\begin{frame}[fragile]
+\frametitle{Data Availability}
 ~\\
 ~\\
-The final community abundance database is publicly available and importable through the EcoData Retriever.\\ 
-(http://www.ecodataretriever.org/)
+Public \& open access through figshare.\\
+EcoData Retriever importable.\\
+\begin{verbatim}
+(http://figshare.com)
+(http://www.ecodataretriever.org)
+\end{verbatim}
+\includegraphics[scale=.3]{./sad-data/dissertation/retriever_logo_wtext.png}
+\includegraphics[scale=.5]{./sad-data/dissertation/figshare_FullColour.jpg}
 \end{frame}
@@
 \frametitle{Forms of the SAD}
-\begin{large}
-Model classes:
-\end{large}
+Statistical description\\  
+\includegraphics[scale=.2]{./sad-data/dissertation/Preston1948.png}\\
+
+\begin{tiny}
+Preston 1962a.\\
+\end{tiny}
+
+Process-based\\
+\includegraphics[scale=.25]{./sad-data/dissertation/Rosindelletal2011.png}\\
+
+\begin{tiny}
+Rosindell et al. 2011.
+\end{tiny}
+\note{
 \begin{itemize}
-\item Purely statistical
-\item Branching process
-\item Population dynamics
-\item Niche partitioning
+\item Purely statistical (Lognormal, logseries)
+\item Branching process (Zipf)
+\item Population dynamics (Neutral theory)
+\item Niche partitioning (Geometric)
 \item Maximum entropy
 \item Feasible set/combinatorics
-\end{itemize}
+\end{itemize}}
 \end{frame}

### 2015-04-02 defense_pres.tex
Does a bunch of things, mostly adding graphics, I think.

@@
 %\logo{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
-\institute{\includegraphics[scale=.07]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.1]{../Miscellaneous/Pictures/Weecology.png}} 
+\institute{\includegraphics[scale=.07]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.35]{./sad-data/dissertation/WeecologyProduction.png}} 
 %\subject{} 
@@
 %\end{frame}
+\section{Usage Notes}
+\begin{frame}
+\frametitle{Open science}
+\begin{itemize}
+\item Code: 
+\begin{itemize}
+\item github.com/embaldridge
+\item github.com/weecology
+\end{itemize}
+\item Data: figshare.com
+\item Twitter: @elitabaldridge
+\end{itemize}
+\includegraphics[scale=.5]{./sad-data/dissertation/Open_Access.png}  
+\includegraphics[scale=.4]{./sad-data/dissertation/osi_logo.png}
+\end{frame}
+
+\begin{frame}[t]
+\begin{huge}
+Feel free to:\\
+\end{huge}
+\includegraphics[scale=.5]{./sad-data/dissertation/use.png}\\
+\begin{huge}
+Provided that:\\
+\end{huge}
+\includegraphics[scale=.5]{./sad-data/dissertation/attribution.png}
+\end{frame}
 
@@
 \end{itemize}
+\includegraphics[scale=.5]{./sad-data/dissertation/generichollowcurves.png}
 \note{
@@
 \end{itemize}
+\end{frame}
+
+\subsection{Signal and Noise}
+\begin{frame}[t]
+\frametitle{Signal \& Noise}
+\begin{center}
+\includegraphics[scale=.4]{./sad-data/dissertation/SignalNoise.png}
+\end{center}
 \end{frame}
@@
 Taxonomic and ecosystem limitations in datasets, e.g.North American terrestrial bias.}
-\end{frame}
-
-\subsection{Signal and Noise}
-\begin{frame}[t]
-\frametitle{Signal \& Noise}
-\begin{center}
-\includegraphics[scale=.4]{./sad-data/dissertation/SignalNoise.png}
-\end{center}
 \end{frame}
@@
 
-\subsection{Data Availability}
+\subsubsection{Data Availability}
 \begin{frame}[fragile]
@@
 (http://www.ecodataretriever.org)
+sad_data = 
+ecoretriever::fetch('MiscAbundanceDB')
 \end{verbatim}
@@
 \frametitle{Acknowledgements}
-~\\ %Adds vertical space for better aesthetics
 Dr. Thomas Price \& USU Student Health Center.\\
 ~\\
-The Flint Hills of Kansas.\\
-~\\
-Tea, electric blankets, \& heating pads.\\
+Tea, heating pads, \& the Flint Hills of Kansas.\\
 ~\\
 A very supportive husband \& family.\\
+~\\
+\begin{Large}
+Publicly available data, \& the citizen scientists that make that possible.\\
+\end{Large}
 \end{frame}

### 2015-04-02 defense_pres.tex
Changes bioregions graph.
Fixes variables table.

@@
 \end{frame}
-
-\subsection{Introduction to Ecoinformatics}
+biog\subsection{Introduction to Ecoinformatics}
 \begin{frame}[t]
@@
 \begin{table}
-\begin{tabular}{l|l} 
- Variable name & Variable definitions\\ 
+\begin{tabular}{l} 
+ Variables collected\\ 
 \hline
- Class & Taxonomic class of species \\
- Family & Taxonomic family of species \\
- Genus & Taxonomic genus of species\\
- Species & Specific epithet of species  \\
- Relative\_abundance & Relative abundance of species \\
- Abundance & Abundance of species \\
- Collection\_Year & Start of collecting \\
- End\_Collection & End of collecting \\
- Site\_Name & Name/description of site \\
- Biogeographic\_region & Biogeographic region \\
- Site\_notes & Additional site information \\ 
+\\
+ Class \\
+ Family\\
+ Genus \\
+ Species (Specific epithet)\\
+ Relative abundance \\
+ Abundance \\
+ Collection Year, starting\\
+ Collection Year, ending \\
+ Site Name \\
+ Biogeographic region \\
+ Site notes\\ 
 \end{tabular}
@@
 \frametitle{Data}
-\includegraphics[scale=.5]{./sad-data/dissertation/bioregions.png}
+\includegraphics[scale=.27]{./sad-data/dissertation/bioregions.png}
 \end{frame}

### 2015-04-02 defense_pres.tex
Expands methods section.

@@
 \end{large}
+\begin{center}
+\includegraphics[scale=.52]{./sad-data/dissertation/genericRAD.png}\\
+\end{center}
+\note{
 \begin{itemize}
@@
 \end{itemize}
-\item Many forms of the species abundance distribution (SAD).
-\end{itemize}
+\end{itemize}}
+Many models of the species abundance distribution (SAD).
 \end{frame}
@@
 \subsection{Forms of the distribution}
-\begin{frame}
-\frametitle{Forms of the SAD}
+\begin{frame}[t]
+\frametitle{SAD models}
 Statistical description\\  
@@
 \subsubsection{Analysis}
-\begin{frame}
+\begin{frame}[t]
 \frametitle{SAD Comparisons}
@@
 \begin{itemize}
-\item Model fitting with maximum likelihood estimation. 
+\item Model fitting with maximum likelihood estimation.\\
+~\\
+$l_x(\theta) = \log h(x) + \log f_\theta(x)$
+\end{itemize}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{SAD Comparisons}
+~\\
+Analysis:
+\begin{itemize}
 \item Likelihood based model selection to compare the fits of the different models.
+\begin{itemize}
+\item Assess the fit of the model without corrections for parameter number or similarity to other models.
+\item How well does the model describe the data?
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{SAD Comparisons}
+~\\
+Analysis:
+\begin{itemize}
 \item Model comparison with corrected Aikaike Information Criterion (AICc) weights.
+\begin{itemize}
+\item Assess the fit of the model correcting for parameter number and small sample size.
+\item How well does the model describe the data relative to the number of parameters?
+\end{itemize}
 \end{itemize}
@@
 \frametitle{SAD Comparisons}
+\includegraphics[scale=.5]{./sad-data/chapter1/Zipf_weights.png}
+\end{frame}
+
+\begin{frame}{}
+\frametitle{SAD Comparisons}
 \includegraphics[scale=.5]{./sad-data/dissertation/AICc_weights.png}
@@
 \includegraphics[scale=.5]{./sad-data/dissertation/likelihoods.png}
+\end{frame}
+
+\begin{frame}{}
+\frametitle{SAD Comparisons}
+\includegraphics[scale= 1]{./sad-data/dissertation/Zipf_one_to_one.png}
 \end{frame}

### 2015-04-02 defense_pres.tex
Adds more logos.

@@
 \end{itemize}
-\includegraphics[scale=.5]{./sad-data/dissertation/Open_Access.png}  
-\includegraphics[scale=.4]{./sad-data/dissertation/osi_logo.png}
+\begin{center}
+\includegraphics[scale=.40]{./sad-data/dissertation/GitHub-Mark-120px-plus.png}
+\includegraphics[scale=.45]{./sad-data/dissertation/figshare_FullColour.jpg} 
+\includegraphics[scale=.2]{./sad-data/dissertation/Open_Access.png}  
+\includegraphics[scale=.15]{./sad-data/dissertation/osi_logo.png}
+
+\end{center}
 \end{frame}

### 2015-04-02 defense_pres.tex
Fixes data table.

@@
 \begin{tabular}{l|c|l|r}
- Dataset &Dataset code &Availability &Total sites\\
+ Dataset &Dataset code &Availability &Sites\\
 \hline
+ Gentry's Forest Transects &Gentry &Public &10355\\
  Breeding Bird Survey &BBS &Public &2769\\
  Christmas Bird Count &CBC &Private &1999\\
- Gentry's Forest Transects &Gentry &Public &10355\\
  Forest Inventory Analysis &FIA	 &Public &220\\
+ N. American Butterfly Count &NABA &Private &400\\
+ Actinopterygii, compiled &Actinopterygii &Public &161\\
+ Reptilia, compiled &Reptilia &Public &138\\
  Mammal Community Database &MCDB &Public &103\\
- N. American Butterfly Count &NABA &Private &400\\
- Actinopterygii, this dissertation	 &Actinopterygii &Public &161\\
- Reptilia, this dissertation &Reptilia &Public &138\\
- Amphibia, this dissertation &Amphibia &Public &43\\
- Coleoptera, this dissertation &Coleoptera &Public &5\\
- Arachnida, this dissertation &Arachnida &Public &25\\
+ Amphibia, compiled &Amphibia &Public &43\\
+ Arachnida, compiled &Arachnida &Public &25\\
+ Coleoptera, compiled &Coleoptera &Public &5\\
 \end{tabular}
-\caption{Datasets used for species-abundance distribution comparisons.
-Datasets marked as Private were obtained through data requests to the providers resulting in Memorandums of Understanding governing data use.}
+\caption{Datasets used for species-abundance distribution comparisons. Datasets marked as Private obtained through data requests to the providers with Memorandums of Understanding.}
 \end{table}

### 2015-04-02 defense_pres.tex
Reworks neutral analysis slides.

@@
 \includegraphics[scale=.25]{./sad-data/dissertation/Rosindelletal2011.png}\\
-
 \begin{tiny}
@@
 \begin{itemize}
-\item Model fitting, log-likelihood, and AICc calculations performed with macroecotools Python package.\\
+\item Model fitting, log-likelihood, \& AICc: macroecotools Python package.\\
 \begin{small}
@@
 \end{small}
-\item All of the analysis code and the majority of the data is publicly available.
+\item All code \& majority of data are publicly available.
 \begin{small}
@@
 \end{itemize}
+\begin{center}
+\includegraphics[scale=.40]{./sad-data/dissertation/GitHub-Mark-120px-plus.png}
+\end{center}
+\end{frame}
+
+\begin{frame}
+\frametitle{Open science}
+\begin{Large}
+More reproducible.\\
+More accessible.\\
+~\\
+\begin{huge}
+\emph{Better science.}
+~\\
+~\\
+\end{huge}
+\end{Large}
+\begin{center}
+\includegraphics[scale=.2]{./sad-data/dissertation/Open_Access.png}  
+\includegraphics[scale=.15]{./sad-data/dissertation/osi_logo.png}
+
+\end{center}
 \end{frame}
@@
 \begin{frame}[t]
-\frametitle{Neutral Analysis}
+\frametitle{Neutral theory}
 ~\\
-The unified neutral theory of biodiversity:\\
+Many formulations, but:
 ~\\
 \begin{itemize}
-\item Multiple formulations.
+\item Species \& individuals ecologically \& demographically equivalent.\\
+\end{itemize}
+\includegraphics[scale=.35]{./sad-data/dissertation/Rosindelletal2011.png}\\
+\begin{tiny}
+Rosindell et al. 2011.
+\end{tiny}
+\note{
 \begin{itemize}
-\item Species and individuals are ecologically and demographically equivalent.\\
+\item Species \& individuals ecologically \& demographically equivalent.\\
 \item Stochastic variation in birth, death, immigration, \& speciation results in species abundance differences.
-\end{itemize}
-\end{itemize}
+\end{itemize}}
 \end{frame}
@@
 \frametitle{Neutral Analysis}
-Early tests of neutral theory based on comparing the fit of empirical species abundance distributions to the neutral prediction.\\
+Early tests of neutral theory compared the fit of empirical species abundance distributions to the neutral prediction.\\
 ~\\
@@
 ~\\
+\begin{Large}
+\emph{However...}
+\end{Large}
 \end{frame}
@@
 Connolly et al. 2014 identified non-neutral species abundance distributions in marine communities.\\
+\begin{center}
+\includegraphics[scale=.25]{./sad-data/dissertation/Connolly2014AB.png}
+\end{center}
+\note{
 \begin{small}
@@
 \end{itemize}
-\end{small}
-~\\
+\end{small}}
 May be a robust method for identifying communities that exhibit non-neutrality.\\
-\begin{tiny}
-Connolly et al. 2014.
-\end{tiny}
 \end{frame}

### 2015-04-03 defense_pres.tex
Moves open science slide.
Reorders, adds slides.

@@
 \setbeamertemplate{enumerate items}[default]
-\author{Elita Baldridge}
+\author{Elita Baldridge\\ @elitabaldridge}
 \title[17pt]{A data-intensive assessment of the species-abundance distribution.}
@@
 \section{Usage Notes}
-\begin{frame}
-\frametitle{Open science}
-\begin{itemize}
-\item Code: 
-\begin{itemize}
-\item github.com/embaldridge
-\item github.com/weecology
-\end{itemize}
-\item Data: figshare.com
-\item Twitter: @elitabaldridge
-\end{itemize}
-\begin{center}
-\includegraphics[scale=.40]{./sad-data/dissertation/GitHub-Mark-120px-plus.png}
-\includegraphics[scale=.45]{./sad-data/dissertation/figshare_FullColour.jpg} 
-\includegraphics[scale=.2]{./sad-data/dissertation/Open_Access.png}  
-\includegraphics[scale=.15]{./sad-data/dissertation/osi_logo.png}
-
-\end{center}
-\end{frame}
-
 \begin{frame}[t]
@@
 
-\section{Introduction}
-\subsection{Commonness & rarity}
-\begin{frame}[t]
-\frametitle{Commonness \& rarity}
-"Who can explain why one species ranges widely, and is very numerous, and why another allied species has a narrow range and is rare?
-Yet these relations are of the highest important, for they determine the present welfare and, as I believe, the future success and modification of every inhabitant of this world."
-
-Darwin, 1859.
-
-\note{
-Few common species.
-Many rare species.
-One of the most fundamental and ubiquitous patterns in ecology.}
+\begin{frame}
+\frametitle{Open science}
+\begin{itemize}
+\item Code: 
+\begin{itemize}
+\item github.com/embaldridge
+\item github.com/weecology
+\end{itemize}
+\item Data: figshare.com
+\end{itemize}
+\begin{center}
+\includegraphics[scale=.40]{./sad-data/dissertation/GitHub-Mark-120px-plus.png}
+\includegraphics[scale=.45]{./sad-data/dissertation/figshare_FullColour.jpg} 
+\includegraphics[scale=.2]{./sad-data/dissertation/Open_Access.png}  
+\includegraphics[scale=.15]{./sad-data/dissertation/osi_logo.png}
+\end{center}
 \end{frame}
 
-\begin{frame}
-Species abundance distribution
-\begin{itemize}
-\item Describes the distribution of commonness \& rarity of species.
-\item Exhibits a hollow curve distribution.
-\end{itemize}
-\includegraphics[scale=.5]{./sad-data/dissertation/generichollowcurves.png}
-\note{
-Relative abundance distribution (RAD)
-Species abundance distribution (SAD)}
-\end{frame}
-
+\section{Introduction}
 \subsection{What is macroecology?}
@@
 \frametitle{Macroecology}
-\normalsize One approach to studying ecological patterns and processes.\\
+\normalsize Search for general patterns \& processes.\\
+\begin{center}
+\includegraphics[scale=.35]{./sad-data/dissertation/PatternProcess_example.png}
+\end{center}
+\note{
 \begin{itemize}
@@
 \end{itemize}
-\item Search for generality.
-\end{itemize}
+\item Search for general patterns \& processes.
+\end{itemize}}
 \end{frame}
 
-\subsection{Signal and Noise}
-\begin{frame}[t]
-\frametitle{Signal \& Noise}
+\begin{frame}
+Species abundance distribution
+\note{
+Few common species.
+Many rare species.
+One of the most fundamental and ubiquitous patterns in ecology.}
+\begin{itemize}
+\item Describes the distribution of commonness \& rarity of species.
+\item Exhibits a hollow curve distribution.
+\end{itemize}
+\includegraphics[scale=.5]{./sad-data/dissertation/generichollowcurves.png}\\
+\begin{itemize}
+\item Many potential pattern-generating mechanisms.
+\end{itemize}
+\note{
+Relative abundance distribution (RAD)
+Species abundance distribution (SAD)}
+\end{frame}
+
+\begin{frame}
+\frametitle{Pattern \& Process;\\ Signal \& Noise}
 \begin{center}
@@
 \end{center}
+\note{
+\begin{Huge}
+\begin{center}
+Pattern\\ 
+\MVArrowDown{}\\  
+Process\\  
+\MVArrowDown{}\\
+Prediction
+\end{center}
+\end{Huge}}
 \end{frame}
 
-\begin{frame}
-\frametitle{Macroecology}
-\begin{Huge}
-\begin{center}
-
-Pattern
-
-\MVArrowDown{}
-
-Process
-
-\MVArrowDown{}
-
-Prediction
-
-\end{center}
-\end{Huge}
-\end{frame}
+\subsection{Commonness & rarity}
+%\begin{frame}[t]
+%\frametitle{Commonness \& rarity}
+%"Who can explain why one species ranges widely, and is very numerous, and why another %allied species has a narrow range and is rare?
+Yet these relations are of the highest %important, for they determine the present welfare and, as I believe, the future success %and modification of every inhabitant of this world."\\
+%~\\ 
+%Darwin, 1859.\\
+%\end{frame}
 
@@
 \begin{itemize}
-\begin{small}
+\item Simultaneous testing of competing models and model predictions with a consistent statistical approach.
 \item Test patterns with multiple taxonomic groups/ecosystems.  
-\item Simultaneous testing of competing models and model predictions with a consistent statistical approach.
-\end{small}
-\end{itemize}
-\end{frame}
-biog\subsection{Introduction to Ecoinformatics}
-\begin{frame}[t]
-\frametitle{The Rules of Ecoinformatics}
-\begin{Large}
-Garbage in, garbage out.\\
-\end{Large}
-\begin{itemize}
-\item All data are good, not all data are appropriate.
-\item Fit the data to the question.
 \end{itemize}
@@
 \includegraphics[scale=.55]{./sad-data/chapter3/presentation_map.png}
-\end{frame}
-
-\begin{frame}[t]{}
-\frametitle{Data}
+\note{
 \begin{large}
@@
 Lots of data in the literature.\\
-\end{large}
+\end{large}}
 \end{frame}
@@
 \subsection{Compiled Data}
-\begin{frame}{}
-\frametitle{Data}
-\includegraphics[scale=.35]{../Miscellaneous/Pictures/Phd/CompiledData.png}
+\subsubsection{Introduction to Ecoinformatics}
+\begin{frame}[t]
+\frametitle{The Rules of Ecoinformatics}
+\begin{Large}
+Garbage in, garbage out.\\
+\end{Large}
+\begin{itemize}
+\item All data are good, not all data are appropriate.
+\item Fit the data to the question.
+\end{itemize}
 \end{frame}
-
 \subsubsection{Data Collection}
@@
 \end{itemize}
-\end{frame}
-
-\begin{frame}[t]
-\frametitle{Data wrangling}
-\begin{center}
-\includegraphics[scale=.27]{./sad-data/dissertation/Wrangling.png}
-\end{center}
-\begin{tiny}
-Cavitt 2000.
-\end{tiny}
 \end{frame}
@@
 
+\begin{frame}[t]
+\frametitle{Data wrangling}
+\begin{center}
+\includegraphics[scale=.27]{./sad-data/dissertation/Wrangling.png}
+\end{center}
+\begin{tiny}
+Cavitt 2000.
+\end{tiny}
+\end{frame}
+
 \subsubsection{Data Summary}
+\begin{frame}{}
+\frametitle{Data}
+\includegraphics[scale=.35]{../Miscellaneous/Pictures/Phd/CompiledData.png}
+\end{frame}
+
 \begin{frame}{}
@@
 Statistical description\\
-\includegraphics[scale=.2]{./sad-data/dissertation/Preston1948.png}\\
-
+\begin{center}  
+\includegraphics[scale=.2]{./sad-data/dissertation/Preston1948.png}
 \begin{tiny}
@@
 \end{tiny}
-
+\end{center}
 Process-based\\
-\includegraphics[scale=.25]{./sad-data/dissertation/Rosindelletal2011.png}\\
+\begin{center}
+\includegraphics[scale=.25]{./sad-data/dissertation/Rosindelletal2011.png}
 \begin{tiny}
-Rosindell et al. 2011.
+Rosindell et al. 2011.\\
 \end{tiny}
+\end{center}
 \note{
@@
 \subsubsection{Data}
+\begin{frame}{}
+\frametitle{Data}
+\includegraphics[scale=.4]{../Miscellaneous/Pictures/Phd/MapCreatures.png}
+\end{frame}
+
 \begin{frame}[shrink=35]
@@
 \end{center}
-\end{frame}
-
-\begin{frame}{}
-\frametitle{Data}
-\includegraphics[scale=.4]{../Miscellaneous/Pictures/Phd/MapCreatures.png}
 \end{frame}
@@
 \item Examine scale dependence of pattern.
+\item More general approach to process.
 \end{itemize}
-~\\
-~\\
-However, identification of mechanism may not be necessary for prediction.
 \end{frame}
@@
 \section{Neutral analysis}
-\begin{frame}[t]
-\frametitle{Neutral theory}
-~\\
-Many formulations, but:
-~\\
-\begin{itemize}
-\item Species \& individuals ecologically \& demographically equivalent.\\
-\end{itemize}
-\includegraphics[scale=.35]{./sad-data/dissertation/Rosindelletal2011.png}\\
-\begin{tiny}
-Rosindell et al. 2011.
-\end{tiny}
-\note{
-\begin{itemize}
-\item Species \& individuals ecologically \& demographically equivalent.\\
-\item Stochastic variation in birth, death, immigration, \& speciation results in species abundance differences.
-\end{itemize}}
-\end{frame}
-
 \begin{frame}
@@
 
+\begin{frame}[t]
+\frametitle{Neutral theory}
+~\\
+Many formulations, but:
+~\\
+\begin{itemize}
+\item Species \& individuals ecologically \& demographically equivalent.\\
+\end{itemize}
+\includegraphics[scale=.35]{./sad-data/dissertation/Rosindelletal2011.png}\\
+\begin{tiny}
+Rosindell et al. 2011.
+\end{tiny}
+\note{
+\begin{itemize}
+\item Species \& individuals ecologically \& demographically equivalent.\\
+\item Stochastic variation in birth, death, immigration, \& speciation results in species abundance differences.
+\end{itemize}}
+\end{frame}
+
 \subsection{Data & Analysis}
@@
 Compared a non-neutral model (Poisson lognormal) to a neutral model (negative binomial).\\
+\end{frame}
+
+\begin{frame}{}
+\frametitle{Neutral Analysis}
+\includegraphics[scale=.43]{./sad-data/dissertation/EmpirModelHist.png}
 \end{frame}
@@
 
-\begin{frame}{}
-\frametitle{Neutral Analysis}
-\includegraphics[scale=.43]{./sad-data/dissertation/EmpirModelHist.png}
-\end{frame}
-
 \subsection{Results}
@@
 \frametitle{Neutral Analysis}
-\includegraphics[scale=.45]{./sad-data/dissertation/distabclasses_vs_lognormwgt.png}
+\includegraphics[scale=.40]{./sad-data/dissertation/avgvals_by_dataset.png}
 \end{frame}
@@
 \frametitle{Neutral Analysis}
-\includegraphics[scale=.40]{./sad-data/dissertation/avgvals_by_dataset.png}
+\includegraphics[scale=.45]{./sad-data/dissertation/distabclasses_vs_lognormwgt.png}
 \end{frame}
@@
 
-\begin{frame}[t]{}
-\frametitle{Conclusions}\
-~\\ 
-\begin{large}
-Predictive macroecology
-\end{large}
-~\\ 
-\begin{itemize}
-\item Traditional approach is pattern to process to prediction.
-\item May be possible to generate robust ecological predictions from general patterns.
-\item Process and prediction may be two separate research goals.
-\end{itemize} 
-\end{frame}
+%\begin{frame}[t]{}
+%\frametitle{Conclusions}\
+%~\\ 
+%\begin{large}
+%Predictive macroecology
+%\end{large}
+%~\\ 
+%\begin{itemize}
+%\item Traditional approach is pattern to process to prediction.
+%\item May be possible to generate robust ecological predictions from general patterns.
+%\item Process and prediction may be two separate research goals.
+%\end{itemize} 
+%\end{frame}
 
@@
 \item Remote access \& participation.\\
+\item Accessibility information
+\note{
 \item Computational tools \& tricks.
@@
 \item Programming skills (data manipulation \& analysis).
-\end{itemize}
+\end{itemize}}
 \end{itemize}

### 2015-04-03 defense_pres.tex
Expands portion on data wrangling.

@@
 \frametitle{Macroecology}
-\normalsize Search for general patterns \& processes.\\
+\normalsize One approach for identifying general ecological patterns \& processes.
 \begin{center}
-\includegraphics[scale=.35]{./sad-data/dissertation/PatternProcess_example.png}
+\includegraphics[scale=.30]{./sad-data/dissertation/SpatialTaxonomic.png}
 \end{center}
@@
 \item Large scales.
+\end{itemize}
 \begin{itemize}
@@
 \end{itemize}
+\begin{itemize}
 \item Search for general patterns \& processes.
@@
 
+\subsection{Let's begin with an example..}
 \begin{frame}
-Species abundance distribution
+\frametitle{Let's begin with an example...}
 \note{
@@
 One of the most fundamental and ubiquitous patterns in ecology.}
+Species abundance distribution (SAD)
 \begin{itemize}
 \item Describes the distribution of commonness \& rarity of species.
+\end{itemize}
+\begin{center}
+\includegraphics[scale=.4]{./sad-data/dissertation/generichollowcurves.png}\\
+\end{center}
+\note{
+\begin{itemize}
+\item Many potential pattern-generating mechanisms.
 \item Exhibits a hollow curve distribution.
 \end{itemize}
-\includegraphics[scale=.5]{./sad-data/dissertation/generichollowcurves.png}\\
-\begin{itemize}
-\item Many potential pattern-generating mechanisms.
-\end{itemize}
-\note{
 Relative abundance distribution (RAD)
 Species abundance distribution (SAD)}
+\end{frame}
+
+\begin{frame}
+\frametitle{Let's begin with an example...}
+\begin{center}
+\includegraphics[scale=.35]{./sad-data/dissertation/PatternProcess_example_text.png}\\
+\end{center}
+\end{frame}
+
+\begin{frame}
+\frametitle{Patterns \& process.}
+\begin{huge}
+\begin{center}
+Process\\ 
+\includegraphics[scale=.35]{./sad-data/dissertation/ProcessesPatterns.png}\\
+Pattern\\
+\end{center}
+\end{huge}
 \end{frame}
@@
 
-\subsection{Commonness & rarity}
+%\subsection{Commonness & rarity}
 %\begin{frame}[t]
@@
 \begin{frame}[t]
-\frametitle{Macroecology}
-Challenges of macroecology\\
+\frametitle{Challenges of macroecology}
 \begin{itemize}
@@
 \begin{frame}[t]
-\frametitle{Macroecology}
-Best practice recommendations\\
+\frametitle{Best practice recommendations}
 \begin{itemize}
-\item Simultaneous testing of competing models and model predictions with a consistent statistical approach.
-\item Test patterns with multiple taxonomic groups/ecosystems.  
+\item Test multiple models with consistent statistical approach.
+\item Test with multiple taxonomic groups/ecosystems.  
 \end{itemize}
+\begin{center}
+\includegraphics[scale=.2]{./sad-data/dissertation/SpatialTaxonomic.png}
+\end{center}
 \end{frame}
@@
 \begin{frame}[t]
-\frametitle{Data}
+\frametitle{Current Data}
 \vspace{-7pt}
@@
 \subsection{Compiled Data}
+\begin{frame}[t]
+\frametitle{Macroecological data}
+Challenges of macroecology\\
+\begin{small}
+\begin{itemize}
+\item Limited number of large datasets.
+\item Lack of identification of process.
+\end{itemize}
+\end{small}
+Best practice recommendations
+\begin{small}
+\begin{itemize}
+\item Test with multiple taxonomic groups/ecosystems. 
+\end{itemize}
+\end{small} 
+\begin{large}
+~\\
+Plenty of data in the literature.
+\end{large}
+\end{frame}
+
 \subsubsection{Introduction to Ecoinformatics}
@@
 \end{frame}
+
+\begin{frame}[t]{}
+\frametitle{Building a database}
+\begin{itemize}
+\item Decide on inclusion criteria.
+\item Decide what variables to collect.
+\item Decide on handling of missing data.
+\item Decide on database structure.
+\item Search for data.
+\item Sort papers into useable and not.
+\item Collect data.
+\end{itemize}
+\begin{center}
+Record decisions at all steps:\\
+~\\
+\begin{large}
+\emph{Metadata are important.}
+\end{large}
+\end{center}
+\end{frame}
+
 \subsubsection{Data Collection}
@@
 
+\subsubsection{Data Wrangling}
 \begin{frame}[t]
@@
 \begin{center}
-\includegraphics[scale=.27]{./sad-data/dissertation/Wrangling.png}
+\includegraphics[scale=.37]{./sad-data/dissertation/WranglingRaw.png}
 \end{center}
-\begin{tiny}
-Cavitt 2000.
-\end{tiny}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Data wrangling}
+\begin{center}
+\includegraphics[scale=.32]{./sad-data/dissertation/WranglingEntry.png}
+\end{center}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Data wrangling}
+\begin{center}
+\includegraphics[scale=.32]{./sad-data/dissertation/WranglingEnd.png}
+\end{center}
 \end{frame}
@@
 \end{itemize}
+\item The model with the greatest AICc weight was the "winner". 
 \end{itemize}
@@
 \item Compare predictions of different models using multiple macroecological patterns simultaneously.\\
+\end{itemize}
+\includegraphics[scale=.3]{./sad-data/dissertation/MacroecologicalPatterns.png}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{SAD Comparisons}
+Identifying pattern generating mechanisms:
+\begin{itemize}
 \item Examine scale dependence of pattern.

### 2015-04-03 defense_pres.tex
Changes some figures, adds some figures.

@@
 \end{itemize}
+\vspace{-7pt}
 \begin{center}
@@
 \vspace{-7pt}
-\includegraphics[scale=.55]{./sad-data/chapter3/presentation_map.png}
+\begin{center}
+\includegraphics[scale=.45]{./sad-data/dissertation/ExistingDataMap.png}
+\end{center}
 \note{
@@
 \begin{frame}[t]{}
-\frametitle{Data}
+\frametitle{Abundance database}
 Inclusion criteria:
@@
 \begin{frame}[shrink=30]
-\frametitle{Data}
+\frametitle{Abundance database}
 \begin{table}
@@
 \begin{frame}{}
-\frametitle{Data}
+\frametitle{Abundance database}
 \includegraphics[scale=.35]{../Miscellaneous/Pictures/Phd/CompiledData.png}
@@
 \begin{frame}{}
-\frametitle{Data}
+\frametitle{Abundance database}
 \includegraphics[scale=.27]{./sad-data/dissertation/bioregions.png}
@@
 \begin{frame}{}
-\frametitle{Data}
+\frametitle{Abundance database}
 \includegraphics[scale=.45]{./sad-data/dissertation/taxa_sites.png}
@@
 \begin{frame}{}
-\frametitle{Data}
+\frametitle{Abundance database}
 \includegraphics[scale=.45]{./sad-data/dissertation/num_taxa.png}
@@
 \includegraphics[scale=.5]{./sad-data/dissertation/figshare_FullColour.jpg}
+\end{frame}
+
+\subsection{Analysis Data}
+\begin{frame}{}
+\frametitle{Data}
+\begin{center}
+\includegraphics[scale=.4]{./sad-data/dissertation/Database.png}
+\end{center}
+\end{frame}
+
+\begin{frame}{}
+\frametitle{Data}
+\includegraphics[scale=.4]{./sad-data/dissertation/AllDatasets.png}
+\end{frame}
+
+\begin{frame}[shrink=35]
+\frametitle{SAD Comparisons}
+\begin{center}
+\begin{table}
+\begin{tabular}{l|c|l|r}
+ Dataset &Dataset code &Availability &Sites\\
+\hline
+ Gentry's Forest Transects &Gentry &Public &10355\\
+ Breeding Bird Survey &BBS &Public &2769\\
+ Christmas Bird Count &CBC &Private &1999\\
+ Forest Inventory Analysis &FIA	 &Public &220\\
+ N. American Butterfly Count &NABA &Private &400\\
+ Actinopterygii, compiled &Actinopterygii &Public &161\\
+ Reptilia, compiled &Reptilia &Public &138\\
+ Mammal Community Database &MCDB &Public &103\\
+ Amphibia, compiled &Amphibia &Public &43\\
+ Arachnida, compiled &Arachnida &Public &25\\
+ Coleoptera, compiled &Coleoptera &Public &5\\
+\end{tabular}
+\caption{Datasets used for species-abundance distribution comparisons. Datasets marked as Private obtained through data requests to the providers with Memorandums of Understanding.}
+\end{table}
+\end{center}
 \end{frame}
@@
 
-\subsubsection{Data}
-\begin{frame}{}
-\frametitle{Data}
-\includegraphics[scale=.4]{../Miscellaneous/Pictures/Phd/MapCreatures.png}
-\end{frame}
-
-\begin{frame}[shrink=35]
-\frametitle{SAD Comparisons}
-\begin{center}
-\begin{table}
-\begin{tabular}{l|c|l|r}
- Dataset &Dataset code &Availability &Sites\\
-\hline
- Gentry's Forest Transects &Gentry &Public &10355\\
- Breeding Bird Survey &BBS &Public &2769\\
- Christmas Bird Count &CBC &Private &1999\\
- Forest Inventory Analysis &FIA	 &Public &220\\
- N. American Butterfly Count &NABA &Private &400\\
- Actinopterygii, compiled &Actinopterygii &Public &161\\
- Reptilia, compiled &Reptilia &Public &138\\
- Mammal Community Database &MCDB &Public &103\\
- Amphibia, compiled &Amphibia &Public &43\\
- Arachnida, compiled &Arachnida &Public &25\\
- Coleoptera, compiled &Coleoptera &Public &5\\
-\end{tabular}
-\caption{Datasets used for species-abundance distribution comparisons. Datasets marked as Private obtained through data requests to the providers with Memorandums of Understanding.}
-\end{table}
-\end{center}
-\end{frame}
-
 \subsection{Results}
@@
 \begin{itemize}
+\item May be biological mechanisms responsible for differences between marine and terrestrial communities.
+\note{
 \item Non-neutral model outperforms the neutral model in marine systems.
-\item Our results suggest marine systems more generally approximated by non-neutral dynamics; terrestrial systems more variable between neutral and non-neutral dynamics.
+\item Our results suggest marine systems more generally approximated by non-neutral dynamics; terrestrial systems more variable between neutral and non-neutral dynamics.}
 \end{itemize}

### 2015-04-04 defense_pres.tex

@@
 \begin{document}
-
-\section{Title}
-\begin{frame}[t]
-\titlepage
-\end{frame}
-
-%\begin{frame}
-%\tableofcontents
-%\end{frame}
 \section{Usage Notes}
@@
 \end{frame}
+
+\section{Title}
+\begin{frame}[t]
+\titlepage
+\end{frame}
+
+%\begin{frame}
+%\tableofcontents
+%\end{frame}
 
@@
 \begin{itemize}
-\item Quantitative abundances
-\item Animals
-\item Complete sampling
-\item Must not be heavily summarized or processed
-\item High degree of taxonomic resolution
-\item Observational
+\item Quantitative abundances (counts).
+\item Complete sampling.
+\item Raw data (not heavily processed).
+\item High degree of taxonomic resolution.
+\item Observational.
 \end{itemize}
@@
  Species (Specific epithet)\\
- Relative abundance \\
  Abundance \\
@@
  Site notes\\
+ Citation\\ 
 \end{tabular}
@@
 
-\begin{frame}
-\frametitle{Open science}
-\begin{Large}
-More reproducible.\\
-More accessible.\\
-~\\
-\begin{huge}
-\emph{Better science.}
-~\\
-~\\
-\end{huge}
-\end{Large}
-\begin{center}
-\includegraphics[scale=.2]{./sad-data/dissertation/Open_Access.png}  
-\includegraphics[scale=.15]{./sad-data/dissertation/osi_logo.png}
-
-\end{center}
-\end{frame}
+%\begin{frame}
+%\frametitle{Open science}
+%\begin{Large}
+%More reproducible.\\
+%More accessible.\\
+%~\\
+%\begin{huge}
+%\emph{Better science.}
+%~\\
+%~\\
+%\end{huge}
+%\end{Large}
+%\begin{center}
+%\includegraphics[scale=.2]{./sad-data/dissertation/Open_Access.png}  
+%\includegraphics[scale=.15]{./sad-data/dissertation/osi_logo.png}
+%\end{center}
+%\end{frame}
 
@@
 \end{itemize}
-\includegraphics[scale=.3]{./sad-data/dissertation/MacroecologicalPatterns.png}
+\begin{center}  
+\includegraphics[scale=.4]{./sad-data/dissertation/MacroecologicalPatterns.png}
+\end{center}
 \end{frame}

### 2015-04-06 defense_pres.tex
Adds accessibility statement generator.
Adds a couple more pictures.

@@
 %\subject{}
+
 \begin{document}
+
 \section{Usage Notes}
 \begin{frame}[t]
-\begin{huge}
+\frametitle{A data-intensive assessment of the species-abundance distribution.}
+\begin{large}
 Feel free to:\\
-\end{huge}
+\end{large}
 \includegraphics[scale=.5]{./sad-data/dissertation/use.png}\\
-\begin{huge}
+\begin{large}
 Provided that:\\
-\end{huge}
+\end{large}
 \includegraphics[scale=.5]{./sad-data/dissertation/attribution.png}
@@
 \section{Introduction}
-\subsection{What is macroecology?}
-\begin{frame}[t]
-\frametitle{Macroecology}
-\normalsize One approach for identifying general ecological patterns \& processes.
-\begin{center}
-\includegraphics[scale=.30]{./sad-data/dissertation/SpatialTaxonomic.png}
-\end{center}
-\note{
-\begin{itemize}
-\item Data intensive.
-\item Large scales.
-\end{itemize}
-\begin{itemize}
-\item Spatial
-\item Temporal
-\item Taxonomic
-\end{itemize}
-\begin{itemize}
-\item Search for general patterns \& processes.
-\end{itemize}}
-\end{frame}
-
 \subsection{Let's begin with an example..}
@@
 \end{huge}
+\end{frame}
+
+\subsection{What is macroecology?}
+\begin{frame}[t]
+\frametitle{Macroecology}
+\normalsize One approach for identifying general ecological patterns \& processes.
+\begin{center}
+\includegraphics[scale=.30]{./sad-data/dissertation/SpatialTaxonomic.png}
+\end{center}
+\note{
+\begin{itemize}
+\item Data intensive.
+\item Large scales.
+\end{itemize}
+\begin{itemize}
+\item Spatial
+\item Temporal
+\item Taxonomic
+\end{itemize}
+\begin{itemize}
+\item Search for general patterns \& processes.
+\end{itemize}}
 \end{frame}
@@
 \frametitle{Building a database}
+\note{
 \begin{itemize}
@@
 \item Collect data.
-\end{itemize}
+\end{itemize}}
 \begin{center}
@@
 \subsection{Data & Analysis}
+\begin{frame}
+\frametitle{SAD Comparisons}
+\begin{center}
+\includegraphics[scale=.35]{./sad-data/dissertation/SpatialTaxonomic.png}
+\end{center}
+\end{frame}
+
 \subsubsection{Model selection}
@@
 \frametitle{Neutral Analysis}
+\frametitle{SAD Comparisons}
+\begin{center}
+\includegraphics[scale=.2]{./sad-data/dissertation/SpatialTaxonomic.png}
+\end{center}
 Used the same data and model fitting approach.\\
@@
 \begin{frame}[t]{}
-\frametitle{Accessibility}
+\frametitle{This dissertation brought to you by:}
+\begin{large}
+Disability accommodations\\
+\end{large}
+Accessibility statement generator
 \begin{center}
-This dissertation brought to you by:
+\includegraphics[scale=.4]{./sad-data/dissertation/trinket-access-generator.png}\\
+https://trinket.io/python/2df3ea45cf
 \end{center}
-\begin{Large}
-Disability accommodations\\
-\end{Large}
-~\\
+\note{
 \begin{itemize}
-\item Remote access \& participation.\\
-\item Accessibility information
-\note{
 \item Computational tools \& tricks.
@@
 \end{itemize}}
-\end{itemize}
 \end{frame}

### 2015-04-09 defense_pres.tex
Reworks slides.

@@
 \frametitle{Let's begin with an example...}
+\begin{center}
+\includegraphics[scale=.4]{./sad-data/dissertation/beetleabunds.png}\\
+\end{center}
+\end{frame}
+
+\begin{frame}
+\frametitle{Let's begin with an example...}
+\begin{center}
+\includegraphics[scale=.4]{./sad-data/dissertation/BeetleRAD.png}\\
+\end{center}
+\end{frame}
+
+\begin{frame}
+\frametitle{Species abundance distribution}
 \note{
@@
 \begin{frame}
-\frametitle{Let's begin with an example...}
+\frametitle{Pattern \& process.}
 \begin{center}
@@
 Process\\ 
-\includegraphics[scale=.35]{./sad-data/dissertation/ProcessesPatterns.png}\\
+\includegraphics[scale=.35]{./sad-data/dissertation/ProcessesPattern.png}\\
 Pattern\\
@@
 \end{huge}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Traditional approach}
+\vspace{-7pt}
+\begin{center}
+\includegraphics[scale=.45]{./sad-data/dissertation/localclose.png}
+\end{center}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Broader approach}
+\vspace{-7pt}
+\begin{center}
+\includegraphics[scale=.45]{./sad-data/dissertation/birdmapclose.png}
+\end{center}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Knowledge gaps}
+\vspace{-7pt}
+\begin{center}
+\includegraphics[scale=.45]{./sad-data/dissertation/birdmap.png}
+\end{center}
 \end{frame}
@@
 \begin{itemize}
-\item Use only a small subset of available models (typically two).
+\item Use a small subset of available models (typically two).
 \item Focus on a single ecosystem or taxonomic group
-\item Fail to use the most appropriate statistical methods. 
+\item Fail to use most appropriate statistical methods. 
 \end{itemize}
@@
 ~\\
-Tea, heating pads, \& the Flint Hills of Kansas.\\
-~\\
 A very supportive husband \& family.\\
@@
 \end{large}
+Tea, heating pads, \& the Flint Hills of Kansas.\\
 Accessibility statement generator

### 2015-04-09 defense_pres.tex
Keeps reworking slides.

@@
 \frametitle{Pattern \& process.}
+\note{
+Few common species.
+Many rare species.
+One of the most fundamental and ubiquitous patterns in ecology.}
+Species abundance distribution (SAD)
+\begin{itemize}
+\item Reveals pattern-generating mechanisms of community structure.
+\end{itemize}
+\begin{center}
+\includegraphics[scale=.4]{./sad-data/dissertation/realistic_even_RAD.png}\\
+\end{center}
+\end{frame}
+
+\begin{frame}
+\frametitle{Pattern \& process.}
 \begin{center}
@@
 \frametitle{Patterns \& process.}
-\begin{huge}
+\begin{Large}
 \begin{center}
@@
 \end{center}
-\end{huge}
+\end{Large}
+\end{frame}
+
+\subsection{What is macroecology?}
+\begin{frame}[t]
+\frametitle{Macroecology}
+\normalsize One approach for identifying general ecological patterns \& processes.
+\begin{center}
+\includegraphics[scale=.30]{./sad-data/dissertation/SpatialTaxonomic.png}
+\end{center}
+\note{
+\begin{itemize}
+\item Data intensive.
+\item Large scales.
+\end{itemize}
+\begin{itemize}
+\item Spatial
+\item Temporal
+\item Taxonomic
+\end{itemize}
+\begin{itemize}
+\item Search for general patterns \& processes.
+\end{itemize}}
 \end{frame}
@@
 
-\subsection{What is macroecology?}
-\begin{frame}[t]
-\frametitle{Macroecology}
-\normalsize One approach for identifying general ecological patterns \& processes.
-\begin{center}
-\includegraphics[scale=.30]{./sad-data/dissertation/SpatialTaxonomic.png}
-\end{center}
-\note{
-\begin{itemize}
-\item Data intensive.
-\item Large scales.
-\end{itemize}
-\begin{itemize}
-\item Spatial
-\item Temporal
-\item Taxonomic
-\end{itemize}
-\begin{itemize}
-\item Search for general patterns \& processes.
-\end{itemize}}
-\end{frame}
-
-\begin{frame}
-\frametitle{Pattern \& Process;\\ Signal \& Noise}
-\begin{center}
-\includegraphics[scale=.4]{./sad-data/dissertation/SignalNoise.png}
-\end{center}
-\note{
-\begin{Huge}
-\begin{center}
-Pattern\\ 
-\MVArrowDown{}\\  
-Process\\  
-\MVArrowDown{}\\
-Prediction
-\end{center}
-\end{Huge}}
-\end{frame}
-
 %\subsection{Commonness & rarity}
@@
 
+\begin{frame}
+\frametitle{Pattern \& Process;\\ Signal \& Noise}
+\begin{center}
+\includegraphics[scale=.4]{./sad-data/dissertation/SignalNoise.png}
+\end{center}
+\note{
+\begin{Huge}
+\begin{center}
+Pattern\\ 
+\MVArrowDown{}\\  
+Process\\  
+\MVArrowDown{}\\
+Prediction
+\end{center}
+\end{Huge}}
+\end{frame}
+
 \subsection{Best practices}
@@
 \end{center}
+\end{frame}
+
+\section{Outline}
+\begin{frame}
+
 \end{frame}
@@
 \begin{frame}[t]
-\frametitle{SAD Comparisons}
-Identifying pattern generating mechanisms:
-\begin{itemize}
-\item Compare predictions of different models using multiple macroecological patterns simultaneously.\\
-\end{itemize}
+\frametitle{Identifying process:}
+\vspace{-7pt}
 \begin{center}
-\includegraphics[scale=.4]{./sad-data/dissertation/MacroecologicalPatterns.png}
+\includegraphics[scale=.3]{./sad-data/dissertation/SpatialTaxonomic.png}
 \end{center}
-\end{frame}
-
-\begin{frame}[t]
-\frametitle{SAD Comparisons}
-Identifying pattern generating mechanisms:
 \begin{itemize}
 \item Examine scale dependence of pattern.
-\item More general approach to process.
+\item More general approach to process?
 \end{itemize}
@@
 \frametitle{Neutral Analysis}
+Connolly et al. 2014 simulated neutral communities.\\
+\begin{center}
+\includegraphics[scale=.25]{./sad-data/dissertation/Connolly2014A.png}
+\end{center}
+\note{
+\begin{small}
+\begin{itemize}
+\item Compared model fits of a non-neutral distribution (Poisson lognormal) to a neutral distribution (negative binomial distribution).\\
+\end{itemize}
+\end{small}}
+Identified a signal of neutrality.\\
+\end{frame}
+
+\begin{frame}
+\frametitle{Neutral Analysis}
 Connolly et al. 2014 identified non-neutral species abundance distributions in marine communities.\\
 \begin{center}
-\includegraphics[scale=.25]{./sad-data/dissertation/Connolly2014AB.png}
+\includegraphics[scale=.25]{./sad-data/dissertation/Connolly2014B.png}
 \end{center}
@@
 \begin{frame}[t]
-\frametitle{Neutral theory}
+\frametitle{Neutral processes}
 ~\\
-Many formulations, but:
+Many formulations of neutral theory, but:
 ~\\
@@
 \end{itemize}}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Non-neutral processes}
+~\\
+Many specific mechanisms, but:
+~\\
+\begin{itemize}
+\item Shape of the abundance distribution due to differences among species.\\
+\end{itemize}
+\begin{center}
+\includegraphics[scale=.2]{./sad-data/dissertation/non-neutral-processes.png}
+\end{center}
 \end{frame}

### 2015-04-09 defense_pres.tex
More resworking of slides.

@@
 
-\subsection{Challenges of macroecology}
-\begin{frame}[t]
-\frametitle{Challenges of macroecology}
-\begin{itemize}
-\item Studies performed with a limited number of large datasets.
-\item Lack of identification of pattern generating mechanisms.
-\end{itemize}
-\note{
-Taxonomic and ecosystem limitations in datasets, e.g.North American terrestrial bias.}
-\end{frame}
-
 \begin{frame}
@@
 
-\subsection{Best practices}
-\begin{frame}[t]
-\frametitle{Best practice recommendations}
-\begin{itemize}
-\item Test multiple models with consistent statistical approach.
-\item Test with multiple taxonomic groups/ecosystems.  
-\end{itemize}
-\vspace{-7pt}
-\begin{center}
-\includegraphics[scale=.2]{./sad-data/dissertation/SpatialTaxonomic.png}
-\end{center}
-\end{frame}
+%\subsection{Challenges of macroecology}
+%\begin{frame}[t]
+%\frametitle{Challenges of macroecology}
+%\begin{itemize}
+%\item Studies performed with a limited number of large datasets.
+%\item Lack of identification of pattern generating mechanisms.
+%\end{itemize}
+%\note{
+%Taxonomic and ecosystem limitations in datasets, e.g.North American terrestrial bias.}
+%\end{frame}
+
+%\subsection{Best practices}
+%\begin{frame}[t]
+%\frametitle{Best practice recommendations}
+%\begin{itemize}
+%\item Test multiple models with consistent statistical approach.
+%\item Test with multiple taxonomic groups/ecosystems.  
+%\end{itemize}
+%\vspace{-7pt}
+%\begin{center}
+%\includegraphics[scale=.2]{./sad-data/dissertation/SpatialTaxonomic.png}
+%\end{center}
+%\end{frame}
 
@@
 \begin{frame}
-
+\frametitle{Data-intensive ecology}
+\begin{itemize}
+\item Leveraging existing ecological data.
+\item The species abundance distribution.
+\item The statistical approach.
+\item The mechanistic approach.
+\end{itemize}
 \end{frame}
 
-\section{Data}
+\section{Leveraging existing ecological data}
 \subsection{Current Data}
@@
 
-\begin{frame}{}
-\frametitle{Abundance database}
-\includegraphics[scale=.45]{./sad-data/dissertation/num_taxa.png}
-\end{frame}
-
 \subsubsection{Data Availability}
@@
 
-\section{Species abundance distribution comparisons}
+\section{SAD comparisons: The statistical approach.}
 \begin{frame}
-\frametitle{SAD Comparisons}
+\frametitle{SAD comparisons: The statistical approach.}
 \begin{large}
@@
 
-\section{Neutral analysis}
+\section{The mechanistic approach: Neutral analysis.}
 \begin{frame}
-\frametitle{Neutral Analysis}
+\frametitle{The mechanistic approach: Neutral analysis.}
 Early tests of neutral theory compared the fit of empirical species abundance distributions to the neutral prediction.\\
@@
 \item Compared model fits of a non-neutral distribution (Poisson lognormal) to a neutral distribution (negative binomial distribution).\\
+\item Distinct abundance values a measure of power related to the number of species in a community to fit models.
 \end{itemize}
@@
 May be a robust method for identifying communities that exhibit non-neutrality.\\
+Untested in terrestrial systems.
 \end{frame}
@@
 \frametitle{Non-neutral processes}
-~\\
+\begin{center}
+\includegraphics[scale=.4]{./sad-data/dissertation/non-neutral-processes.png}\\
+\end{center}
 Many specific mechanisms, but:
@@
 \end{itemize}
-\begin{center}
-\includegraphics[scale=.2]{./sad-data/dissertation/non-neutral-processes.png}
-\end{center}
 \end{frame}
@@
 \begin{itemize}
+\item Demonstrates the importance of testing with multiple ecosystems.
+\end{itemize}
+\note{
+\begin{itemize}
 \item Results consistent with our species abundance distribution model comparisons. 
@@
 \end{itemize}
-\end{itemize}
+\end{itemize}}
 \end{frame}
@@
 
+\begin{frame}{}
+\frametitle{Abundance database}
+\includegraphics[scale=.45]{./sad-data/dissertation/num_taxa.png}
+\end{frame}
+
 \end{document}

### 2015-04-09 defense_pres.tex
More reworking.

@@
 \subsection{Let's begin with an example..}
-\begin{frame}
-\frametitle{Let's begin with an example...}
-\begin{center}
-\includegraphics[scale=.4]{./sad-data/dissertation/beetleabunds.png}\\
-\end{center}
-\end{frame}
-
 \begin{frame}
@@
 
-\begin{frame}[t]
-\frametitle{Knowledge gaps}
-\vspace{-7pt}
-\begin{center}
-\includegraphics[scale=.45]{./sad-data/dissertation/birdmap.png}
-\end{center}
-\end{frame}
-
 %\subsection{Commonness & rarity}
@@
 \begin{itemize}
-\item Limited number of large datasets.
 \item Lack of identification of process.
@@
 \end{center}
-\note{
-\begin{itemize}
-\item Purely statistical (Lognormal, logseries)
-\item Branching process (Zipf)
-\item Population dynamics (Neutral theory)
-\item Niche partitioning (Geometric)
-\item Maximum entropy
-\item Feasible set/combinatorics
-\end{itemize}}
 \end{frame}
@@
 \item Model fitting with maximum likelihood estimation.\\
+\begin{itemize}
+\item For a given model, estimates model parameters that provide the most likely characterization of the data.
+\item Best practice for fitting species abundance distributions. \begin{tiny} Matthews \& Whittaker 2014.\end{tiny}
+\end{itemize}
 ~\\
-$l_x(\theta) = \log h(x) + \log f_\theta(x)$
+%$l_x(\theta) = \log h(x) + \log f_\theta(x)$
 \end{itemize}
@@
 \begin{itemize}
-\item Assess the fit of the model without corrections for parameter number or similarity to other models.
 \item How well does the model describe the data?
@@
 \begin{itemize}
-\item Assess the fit of the model correcting for parameter number and small sample size.
 \item How well does the model describe the data relative to the number of parameters?
 \end{itemize}
-\item The model with the greatest AICc weight was the "winner". 
+\item The best fitting model had the greatest AICc weight. 
 \end{itemize}
@@
 \item Logseries provides a good naive model for fitting SADs.\\
+\note{
 \begin{itemize}
@@
 \item Best overall model.
-\end{itemize}
+\end{itemize}}
 \end{itemize}
@@
 \section{The mechanistic approach: Neutral analysis.}
-\begin{frame}
-\frametitle{The mechanistic approach: Neutral analysis.}
-Early tests of neutral theory compared the fit of empirical species abundance distributions to the neutral prediction.\\
-~\\
-Later tests suggested species abundance comparisons were insufficient for a rigorous test of neutrality.\\
-~\\
-\begin{Large}
-\emph{However...}
-\end{Large}
-\end{frame}
-
-\begin{frame}
-\frametitle{Neutral Analysis}
-Connolly et al. 2014 simulated neutral communities.\\
-\begin{center}
-\includegraphics[scale=.25]{./sad-data/dissertation/Connolly2014A.png}
-\end{center}
-\note{
-\begin{small}
-\begin{itemize}
-\item Compared model fits of a non-neutral distribution (Poisson lognormal) to a neutral distribution (negative binomial distribution).\\
-\item Distinct abundance values a measure of power related to the number of species in a community to fit models.
-\end{itemize}
-\end{small}}
-Identified a signal of neutrality.\\
-\end{frame}
-
-\begin{frame}
-\frametitle{Neutral Analysis}
-Connolly et al. 2014 identified non-neutral species abundance distributions in marine communities.\\
-\begin{center}
-\includegraphics[scale=.25]{./sad-data/dissertation/Connolly2014B.png}
-\end{center}
-\note{
-\begin{small}
-\begin{itemize}
-\item Compared model fits of a non-neutral distribution (Poisson lognormal) to a neutral distribution (negative binomial distribution).\\
-\end{itemize}
-\end{small}}
-May be a robust method for identifying communities that exhibit non-neutrality.\\
-Untested in terrestrial systems.
-\end{frame}
-
+\subsection{Neutral & non-neutral processes}
 \begin{frame}[t]
@@
 
+\subsection{Neutral Analysis}
+\begin{frame}
+\frametitle{The mechanistic approach: Neutral analysis.}
+Early tests of neutral theory compared the fit of empirical species abundance distributions to the neutral prediction.\\
+~\\
+Later tests suggested species abundance comparisons were insufficient for a rigorous test of neutrality.\\
+~\\
+\begin{Large}
+\emph{However...}
+\end{Large}
+\end{frame}
+
+\begin{frame}
+\frametitle{Neutral Analysis}
+Connolly et al. 2014 simulated neutral communities.\\
+\begin{center}
+\includegraphics[scale=.4]{./sad-data/dissertation/Connolly2014A.png}
+\end{center}
+\note{
+\begin{small}
+\begin{itemize}
+\item Compared model fits of a non-neutral distribution (Poisson lognormal) to a neutral distribution (negative binomial distribution).\\
+\item Distinct abundance values a measure of power related to the number of species in a community to fit models.
+\end{itemize}
+\end{small}}
+Identified a signal of neutrality.\\
+\end{frame}
+
+\begin{frame}
+\frametitle{Neutral Analysis}
+Connolly et al. 2014 identified non-neutral species abundance distributions in marine communities.\\
+\begin{center}
+\includegraphics[scale=.4]{./sad-data/dissertation/Connolly2014B.png}
+\end{center}
+\note{
+\begin{small}
+\begin{itemize}
+\item Compared model fits of a non-neutral distribution (Poisson lognormal) to a neutral distribution (negative binomial distribution).\\
+\end{itemize}
+\end{small}}
+May be a robust method for identifying communities that exhibit non-neutrality.\\
+Untested in terrestrial systems.
+\end{frame}
+
 \subsection{Data & Analysis}
@@
 Used the same data and model fitting approach.\\
-Compared a non-neutral model (Poisson lognormal) to a neutral model (negative binomial).\\
+\end{frame}
+
+\begin{frame}{}
+\frametitle{Neutral Analysis}
+Non-neutral model (Poisson lognormal)\\
+\begin{itemize}
+\item Describes communities generated by non-neutral processes.
+\end{itemize}
+Neutral model (negative binomial).\\
+\begin{itemize}
+\item Describes communities generated by neutral processes.
+\end{itemize}
 \end{frame}
@@
 \frametitle{Neutral Analysis}
-\includegraphics[scale=.43]{./sad-data/dissertation/Connolly2014AB.png}
+\begin{center}
+\includegraphics[scale=.43]{./sad-data/dissertation/Connolly2014B.png}
+\end{center}
 \begin{tiny}
@@
 \end{itemize}
-\note{
-\begin{itemize}
-\item Results consistent with our species abundance distribution model comparisons. 
-\item Results different from Connolly et al. 2014.
-\begin{itemize}
-\item May be biological mechanisms responsible for differences between marine and terrestrial communities.
-\note{
-\item Non-neutral model outperforms the neutral model in marine systems.
-\item Our results suggest marine systems more generally approximated by non-neutral dynamics; terrestrial systems more variable between neutral and non-neutral dynamics.}
-\end{itemize}
-\end{itemize}}
 \end{frame}
@@
 ~\\ 
-\frametitle{Conclusions}\
+\frametitle{A data-intensive approach}\
 Challenging to infer process from species abundance distributions alone.
@@
 \begin{itemize}
-\item Multiple mechanisms proposed for each SAD formulation.
 \item Broad model categorization (i.e. neutral or non-neutral) may be more productive.
@@
 \begin{frame}[t]{}
-\frametitle{Conclusions}\
+\frametitle{A data-intensive approach}\
 ~\\ 
@@
 \includegraphics[scale=.3]{../Miscellaneous/Pictures/Phd/whiteboard.png}
-\begin{tiny}
-(especially Xiao Xiao \& Ken Locey (creator of the whiteboard))
-\end{tiny}
+\begin{small}
+(especially Xiao Xiao \& Ken Locey \begin{tiny}(creator of the whiteboard)\end{tiny})
+\end{small}
 \end{frame}
@@
 \begin{center}
-\includegraphics[scale=.4]{./sad-data/dissertation/trinket-access-generator.png}\\
+\includegraphics[scale=.35]{./sad-data/dissertation/trinket-access-generator.png}\\
 https://trinket.io/python/2df3ea45cf

### 2015-04-15 defense_pres.tex
Condenses example slides.
Tweaks.
Shrinks one figure that was running off the edge.
Moves open science slide to the end.
Swaps slides, changes picture.
Rearranges slide.
Changes pictures to more realistic example beetle SAD.

@@
 
-\begin{frame}
-\frametitle{Open science}
-\begin{itemize}
-\item Code: 
-\begin{itemize}
-\item github.com/embaldridge
-\item github.com/weecology
-\end{itemize}
-\item Data: figshare.com
-\end{itemize}
-\begin{center}
-\includegraphics[scale=.40]{./sad-data/dissertation/GitHub-Mark-120px-plus.png}
-\includegraphics[scale=.45]{./sad-data/dissertation/figshare_FullColour.jpg} 
-\includegraphics[scale=.2]{./sad-data/dissertation/Open_Access.png}  
-\includegraphics[scale=.15]{./sad-data/dissertation/osi_logo.png}
-\end{center}
-\end{frame}
-
 \section{Introduction}
@@
 \begin{center}
-\includegraphics[scale=.4]{./sad-data/dissertation/BeetleRAD.png}\\
+\includegraphics[scale=.25]{./sad-data/dissertation/BeetleRAD.png}\\
 \end{center}
@@
 \begin{frame}
-\frametitle{Species abundance distribution}
-\note{
-Few common species.
-Many rare species.
-One of the most fundamental and ubiquitous patterns in ecology.}
-Species abundance distribution (SAD)
-\begin{itemize}
-\item Describes the distribution of commonness \& rarity of species.
-\end{itemize}
+\frametitle{Let's begin with an example...}
 \begin{center}
-\includegraphics[scale=.4]{./sad-data/dissertation/generichollowcurves.png}\\
+\includegraphics[scale=.25]{./sad-data/dissertation/BeetleRAD_w_graph.png}\\
 \end{center}
-\note{
-\begin{itemize}
-\item Many potential pattern-generating mechanisms.
-\item Exhibits a hollow curve distribution.
-\end{itemize}
-Relative abundance distribution (RAD)
-Species abundance distribution (SAD)}
 \end{frame}
@@
 Species abundance distribution (SAD)
+\begin{center}
+\includegraphics[scale=.4]{./sad-data/dissertation/realistic_even_RAD.png}\\
+\end{center}
 \begin{itemize}
@@
 \end{itemize}
+\note{
+Few common species.
+Many rare species.
+One of the most fundamental and ubiquitous patterns in ecology.
+Species abundance distribution (SAD)
+\begin{itemize}
+\item Describes the distribution of commonness \& rarity of species.
+\end{itemize}
 \begin{center}
-\includegraphics[scale=.4]{./sad-data/dissertation/realistic_even_RAD.png}\\
+\includegraphics[scale=.4]{./sad-data/dissertation/generichollowcurves.png}\\
 \end{center}
+\begin{itemize}
+\item Many potential pattern-generating mechanisms.
+\item Exhibits a hollow curve distribution.
+\end{itemize}
+Relative abundance distribution (RAD)
+Species abundance distribution (SAD)}
 \end{frame}
@@
 \item Raw data (not heavily processed).
-\item High degree of taxonomic resolution.
 \item Observational.
@@
 \frametitle{SAD Comparisons}
-\includegraphics[scale=.5]{./sad-data/dissertation/likelihoods_one_to_one.png}
+\includegraphics[scale=.43]{./sad-data/dissertation/likelihoods_one_to_one.png}
 \end{frame}
@@
 
+\begin{frame}
+\frametitle{Open science}
+\begin{itemize}
+\item Code: 
+\begin{itemize}
+\item github.com/embaldridge
+\item github.com/weecology
+\end{itemize}
+\item Data: figshare.com
+\end{itemize}
+\begin{center}
+\includegraphics[scale=.40]{./sad-data/dissertation/GitHub-Mark-120px-plus.png}
+\includegraphics[scale=.45]{./sad-data/dissertation/figshare_FullColour.jpg} 
+\includegraphics[scale=.2]{./sad-data/dissertation/Open_Access.png}  
+\includegraphics[scale=.15]{./sad-data/dissertation/osi_logo.png}
+\end{center}
+\end{frame}
+
 %\begin{frame}[t]{}

### 2015-04-16 misc-data-query.py
Changes findall to re.findall.

@@ -19,7 +19,7 @@ con.text_factory = str
 #Query for communities that are in the misc main database and have integer abundances
 #Query for taxa
 taxa = cur.execute("""SELECT DISTINCT Class FROM miscabundancedb_main
-                      WHERE Class IS NOT 'Chondrichthyes' AND Class IS NOT 'Aves'
+                      WHERE Class IS NOT 'Chondrichthyes' AND Class IS NOT 'Aves' AND Class is NOT ''
                       ORDER BY Class""") #Excludes Chondrichthyes because that class has too few species. (2, for 2 sites), and Aves, because it has no integer abundance data."
 taxa = cur.fetchall()
 
@@ -35,7 +35,7 @@ con.close()
 
 for taxa_class in taxa:
     taxon_str = str(taxa_class)
-    taxon = findall(r"\'([A-Za-z]+)\'", taxon_str) #Strips out just the taxon name
+    taxon = re.findall(r"\'([A-Za-z]+)\'", taxon_str) #Strips out just the taxon name
     #Run through communities, pull out all data that matches the taxon and output as a .csv
     #Output abundances
     output_file = './sad-data/chapter1/' + taxon[0] + '_spab.csv'

### 2015-04-17 sad-comparison-graphs.py
Removes dependency for SQLalchemy, gets data read into dataframe, pivot tablestill has unexpected keyword argument.

@@ -6,7 +6,6 @@ import matplotlib.pyplot as plt
 import numpy as np
 import sqlite3 as dbapi
 import pandas as pd
-import sqlalchemy
 
 # Set up database capabilities 
 # Set up ability to query data
@@ -1249,16 +1248,12 @@ fileName = "./sad-data/chapter1/zipf_relative.png"
 plt.savefig(fileName, format="png" )
 plt.close()
 
-# Close connection
-con.close()
-
 # 1:1 plots showing log-series likelihoods vs those of other models
 
 plt.figure()
-engine = sqlalchemy.create_engine('sqlite:///sad-data/chapter1/SummarizedResults.sqlite')
-likelihood_data = pd.read_sql_query("""SELECT dataset_code, site, model_name, value
+likelihood_data = pd.read_sql("""SELECT dataset_code, site, model_name, value
                                        FROM RawResults
-                                       WHERE value_type = 'likelihood'""", engine)
+                                       WHERE value_type = 'likelihood'""", con)
 pivoted_likelihoods = pd.pivot_table(likelihood_data, values='value',
                                      index=['dataset_code', 'site'],
                                      columns=['model_name'])
@@ -1283,3 +1278,6 @@ num_sites_by_set_and_model = likelihood_data.groupby(['dataset_code', 'model_nam
 percent_null = null_likes_by_set_and_model / num_sites_by_set_and_model * 100
 print("Data on percent of null likelihoods by model and dataset:\n")
 print percent_null['site'].dropna()
+
+# Close connection
+con.close()

### 2015-04-17 defense_pres.tex
Changes graphs for abundance database to reflect the fixes.
Updates graphs, site numbers.

@@
  Actinopterygii, compiled &Actinopterygii &Public &161\\
- Reptilia, compiled &Reptilia &Public &138\\
+ Reptilia, compiled &Reptilia &Public &129\\
  Mammal Community Database &MCDB &Public &103\\
@@
 
-\begin{frame}{}
-\frametitle{Abundance database}
-\includegraphics[scale=.45]{./sad-data/dissertation/num_taxa.png}
-\end{frame}
-
 \end{document}

### 2015-04-17 sad-comparison-graphs.py
Adds close graphs statement.

@@ -6,6 +6,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import sqlite3 as dbapi
 import pandas as pd
+import sqlalchemy
 
 # Set up database capabilities 
 # Set up ability to query data
@@ -1268,6 +1269,7 @@ for i, model in enumerate(models):
     plt.ylabel(model + " likelihood")
 plt.xlabel("Log-series likelihood")
 plt.savefig("./sad-data/chapter1/likelihoods_one_to_one.png")
+plt.close()
 
 
 # Percent null likelihoods

### 2016-11-08 peerj_response_letter.md
First draft of revision for PeerJ

Dear Sara,

My apologies for the long delay in returning this ms. The lead author has been
unable to work on this and it took me a while to carve out the time to complete
the revision.

We thank you and the reviewers for your kind words and helpful suggestions. We
have worked hard to improve the manuscript in response to these
comments. Our responses are described in detail below.

Regards,
Ethan White

Reviewer 1 (Matheus Lima Ribeiro)

> L. 64: Authors show Table 1, but did not cite it across the text. Please,
> provide citation for table 1.

Two references to Table 1 have been added to the text.

> L. 101-102: the sentence “best practices” is duplicated in this phrase.

This sentence has been simplified to remove the duplication.

> L. 103-104: the word “therefore” is also duplicated in this phrase.

We have removed the duplication.

> Title of Fig. 3: “Number of cases IN WHICH each model…” instead of “where”;

Changed.

> Idem Fig. 4!

Changed.

> L. 184: word “the” is duplicated;

Fixed.

> L. 187: “negative-binomial” instead of “negatvie-binomial”;

Fixed.

> In introduction (L. 34-39), authors justify one of the basic flaw of other
> studies about SADs is that they “use only a small subset of available
> models”. Next (L. 40), the authors describe the study’s goal and say that
> compared the performance of four SADs models. If one key question of
> investigation relates with the fitness of models, why that authors did not
> considered ALL existing SAD models in their analyses? These four chosen models
> often present the best performances (by the discussion, it seems that not!)?
> In methods, the authors justify their choice (the models describe discrete
> distribution, matching the type of data), but these questions remain unclear.

We selected models based on three criteria:

1. They needed to be proper, discrete, models for the SAD
2. They needed to have probability mass functions so that we could compare the
   likelihoods of the model, which eliminates all models that can only be
   described by simulation rules.
3. We prioritized models that represented an array of underlying process types
4. We wanted models that were commonly used in the ecological literature

While these were all described in the original manuscript, the descriptions were
scattered throughout the manuscript and we agree that our thinking on model
choice was unclear. We now start the Model section of the paper with a detailed
explanation of the justifications for the models we chose to work with.

> In methods, authors start saying that compiled a wide array of data sets from
> multiple sources and for multiple taxonomic groups, but do not say which kind
> of data they obtained. Are these data species occurrence records, species
> richness, population abundance…? Which is the temporal range of data? This is
> not clear in the text.

More details have been added in the opening paragraph. All data are full samples
of a given taxonomic assemblage and most data is for a single year. Additional
details are available in the provided citations.

> In lines 62-63 and 67-68, authors say that abundances were computed using
> counts of individuals. However, besides omit the kind of sampled raw data set,
> it is not clear what are the sampling units. For example, have the authors
> split the study area in grid cells (please, describe cell resolution)? Or the
> sampling units were ecoregions…?

More details have been added in the opening paragraph. In the vast majority of
cases the data is at the site level as defined by the data source

> L. 121-126: instead of just describe the list of R-packages used to perform
> analyses, please, describe which analyses were performed using each
> R-package. If possible, please, describe also the functions from each package
> used to perform analyses. A detailed description is a general practice from
> R-modelers and would clear the description of your methods.

We are quite experienced with best practices for presenting reproducible results
and I disagree quite strongly that best practice in this space involves filling
the methods section with lengthy descriptions of how individual functions from
individual packages are used to analyze individual results. The appropriate
place for that level of detail is in the openly available code associated with
an analysis. Our code is publicly available under open source licenses:
https://github.com/weecology/sad-comparison and we will archive this repository
on Zenodo as part of the publication of this paper. It can be run by anyone to
replicate our results and read to look up individual function use if desired.

> L.172-174: I do not agree with this sentence. The authors did not compare
> model fitting between “fully” and “incompletely” sampled communities. It seems
> that authors considered all communities in their analyses, regardless of
> sampling effort. Thus, the presence of “fully censused” communities in this
> study may have negatively affected the fitness of Zipf models. Instead
> comparing the results of this study with other studies (especially Ulrich et
> al. 2010), I invite the authors to discuss about the implications of quality
> of data sets on model fitting;

As detailed in the sentences following lines 172-174 this argument is based on
comparing datasets that are very well sampled with those that are not. Ours come
in large aggregations that are also associated with taxonomic groups, but
none-the-less the comparison is very similar in concept to Ulrich et al. in that
they have a bunch of datasets some of which are determined to be fully censused
and some which are determined to be incomplete. In our case this is based on
meaningful differences in sampling methodology that are discussed in the
associated paragraph. In short, we don't understand the objection.

If the suggestion being made is that we use methods similar to those in Ulrich
et al., then we would note that there are serious issues with those methods that
effectively guarantee the results seen in that paper, because the methods used
for determining the degree of sampling are based on the shape of the abundance
distribution itself.

> L. 209-210: the author did not analyze the double geometric model in this
> study, so it is not a reasonable option to conclude that its performance
> appears to present minor difference with log-series, lognormal and negative
> binomial. This is speculation not supported by analyses;

This paragraph begins with "In combination, the results of these three papers
suggest..." This statement is based on the results of Alroy (2015) in
combination with our results.

> L. 214-216: this is an excellent conclusion from this study! It is supported
> by analyses performed here and yet considerate that found in
> literature. Please, develop all the discussion on this way and avoid
> unsupported speculations.

We thank the review for their kind words. As detailed above we do not believe
that we have engaged in "unsupported speculations" anywhere in the paper. We are
simply doing our best to fully engage with the existing literature within the
limits imposed by our analyses.

## Reviewer 2 (Anonymous)

> The paper is very 'self-contained' with clear, focused goals that are reported
> and discussed in context to previous work. The data is made open when
> possible. The english language is good, in some cases it could a shortened but
> the manuscript is already short so this is not a problem.

Thanks!

> Label sizes of Figure 4 should be increased if the plot is intended to be this
> size in the final article.

We will work with PeerJ to make sure the sizes are appropriate should the paper
be accepted.

> The experimental design is transparent and simple, and well-described. The
> knowledge gap is clearly stated, although in this case it is more of an
> 'information gap' that is filled by comparing more data sets. The authors
> improve on previous work by gathering more data sets and testing a greater
> number of SAD models, which is good.

Thanks!

> The statistical methods are appropriate, the results seem solid and are well
> presented.

Thanks!

> However, since each dataset reports findings from one taxa, I don't know how
> certain it is to state that the SAD is different for different taxa. This
> might just be an artifact of the sampling method within each dataset which is
> correlated to taxa. The authors discuss that trees are fully sampled yet the
> selected SAD model is different for both of them (log-series for fia,
> log-series and poisson for gentry, figure 4, lines 176-177).

We agree with the limitation mentioned here and have added clarifying sentences
to end of the 2nd paragraph of the Discussion and the end of the third paragraph
of the Results.

> Are there datasets with several taxa that could be analysed? It would be
> interesting to break data up into sub-taxa within each category to assess if
> there are some general trends in SAD among subtaxa within a single taxa. For
> example, separate birds into passerines, parrots, falcons, pigeons, loons,
> etc, and see if the SAD model varies by subtaxa. Or by geographical regions.

These are definitely cool ideas and are things we've discussed, but we believe
they are more appropriate for a follow up analysis. We are unlikely to get to
this anytime soon, but would be happy to support anyone interested in
undertaking the effort.

> The article is clearly and concisely written. It set out clear goals and
> fulfilled them. As the authors state in the conclusion, there are clearly more
> detailed ways to analyse the SAD, with multiple macroecological patterns or
> second-order effects, but that was not their goal.

Thanks for the very kind, helpful, and positive review.

> 162 two parameter-model performing

Fixed.

> 184 remove one the

Fixed.

> 186 that the

Fixed.

> 187 negative

Fixed.

> 189 demonstrate

Fixed.

> 192 two analyses

Fixed.

> 200 showed that

Fixed.

> 207 those papers?

We prefer the original phrasing.

> 217 emphasize the challenge

We have changed this to "emphasizes the challenge" since "emphasize" is
associated with the "relatively similar fit" not with "distributions".

### 2016-11-09 sad-postprocess.R
spell 'distribution' correctly

@@ -165,14 +165,14 @@ fancify_names = function(df){
 
 deviance_diff = (deviances[, is_dev] - rowMeans(deviances[, is_dev])) %>%
   fancify_names()
-deviance_diff_long = gather(deviance_diff, key = "Distriution", value = "deviance")
+deviance_diff_long = gather(deviance_diff, key = "Distribution", value = "deviance")
 
 
 AICc_diff = (deviances[, is_AICc] - rowMeans(deviances[, is_AICc])) %>%
   fancify_names()
-AICc_diff_long = gather(AICc_diff, key = "Distriution", value = "AICc")
+AICc_diff_long = gather(AICc_diff, key = "Distribution", value = "AICc")
 
-dev_plot = ggplot(deviance_diff_long, aes(x = Distriution, y = deviance)) + 
+dev_plot = ggplot(deviance_diff_long, aes(x = Distribution, y = deviance)) + 
   geom_hline(yintercept = 0) + 
   geom_violin() + 
   theme_bw() + 
@@ -180,14 +180,14 @@ dev_plot = ggplot(deviance_diff_long, aes(x = Distriution, y = deviance)) +
 my_ggsave(name = "deviance.png", dev_plot)
 
 
-ll_plot = ggplot(deviance_diff_long, aes(x = Distriution, y = -deviance/2)) + 
+ll_plot = ggplot(deviance_diff_long, aes(x = Distribution, y = -deviance/2)) + 
   geom_hline(yintercept = 0) + 
   geom_violin() + 
   theme_bw() + 
   ylab("Deviation from mean log-likelihood")
 my_ggsave(name = "loglik.png", ll_plot)
 
-aic_plot = ggplot(AICc_diff_long, aes(x = Distriution, y = AICc)) + 
+aic_plot = ggplot(AICc_diff_long, aes(x = Distribution, y = AICc)) + 
   geom_hline(yintercept = 0) + 
   geom_violin() + 
   theme_bw() + 
@@ -197,7 +197,7 @@ my_ggsave(name = "aic.png", aic_plot)
 relative_likelihoods = (exp(-deviance_diff / 2) / rowSums(exp(-deviance_diff / 2)))  %>%
   fancify_names()
 relative_likelihoods_long = gather(relative_likelihoods, 
-                                   key = Distriution, 
+                                   key = Distribution, 
                                    value = relative_likelihood)
 
 
@@ -205,21 +205,21 @@ relative_likelihoods_long = gather(relative_likelihoods,
[…]

### 2016-11-10 sad-postprocess.R
fix figure 4

@@ -279,17 +279,22 @@ apply(AICc_diff, 1, which.min) %>%
           las = 1, space = 0)
 dev.off()
   
-png("wins-by-dataset.png", width = 4000, height = 2100, res = 300)
-par(mar =  c(5, 5, 4, 2) + 0.1)
-par(mgp = c(3.5,1,0))
-par(mfrow = c(3, 4))
-for (df in deviance_list) {
-  df %>%
-    select(matches("AICc")) %>%
-    apply(1, which.min) %>% 
-    get_names() %>% 
-    table() %>% 
-    barplot(ylab = "Number of wins", xlab = "Species abundance distribution", las = 1, space = 0)
-  title(df$id[[1]])
-}
-dev.off()
+winners_df = deviances %>% 
+  by_row(~names(which.min(.x[ , grepl("AICc", names(.x))])), .to = "winner", .collate = "cols") %>% 
+  group_by(id, winner) %>% 
+  summarize(wins = n()) %>% 
+  mutate(N = sum(wins)) %>% 
+  mutate(panel = LETTERS[1 + (N < 1E3) + (N < 1E2)]) %>% 
+  mutate(winner = fancify(winner))
+
+library(dichromat)
+
+ggplot(winners_df, aes(x = winner, y = wins, fill = factor(winner))) + 
+  geom_bar(stat = "identity") +
+  facet_wrap(~id, nrow = 4, scales = "free_y") + 
+  cowplot::theme_cowplot() + 
+  xlab("Species abundance distribution") + 
+  ylab("Number of wins") + 
+  scale_fill_manual(values = colorschemes$SteppedSequential.5[c(1, 6, 11, 16)],
+                    guide = FALSE)
+ggsave("wins-by-dataset.png", width = 11, height = 6)

### 2016-11-10 sad-postprocess.R
fix dependency issue

@@ -280,7 +280,7 @@ apply(AICc_diff, 1, which.min) %>%
 dev.off()
   
 winners_df = deviances %>% 
-  by_row(~names(which.min(.x[ , grepl("AICc", names(.x))])), .to = "winner", .collate = "cols") %>% 
+  purrr::by_row(~names(which.min(.x[ , grepl("AICc", names(.x))])), .to = "winner", .collate = "cols") %>% 
   group_by(id, winner) %>% 
   summarize(wins = n()) %>% 
   mutate(N = sum(wins)) %>% 

### 2016-11-10 sad-postprocess.R
more color

@@ -2,6 +2,9 @@ library(dplyr)
 library(ggplot2)
 library(tidyr)
 library(magrittr)
+library(dichromat)
+
+colors = colorschemes$SteppedSequential.5[c(1, 6, 11, 16)]
 
 if (!dir.exists("violins")) {
   dir.create("violins")
@@ -172,25 +175,28 @@ AICc_diff = (deviances[, is_AICc] - rowMeans(deviances[, is_AICc])) %>%
   fancify_names()
 AICc_diff_long = gather(AICc_diff, key = "Distribution", value = "AICc")
 
-dev_plot = ggplot(deviance_diff_long, aes(x = Distribution, y = deviance)) + 
+dev_plot = ggplot(deviance_diff_long, aes(x = Distribution, y = deviance, fill = Distribution)) + 
   geom_hline(yintercept = 0) + 
   geom_violin() + 
   theme_bw() + 
+  scale_fill_manual(values = colors, guide = FALSE) +
   ylab("Deviation from mean deviance (lower is better)")
 my_ggsave(name = "deviance.png", dev_plot)
 
 
-ll_plot = ggplot(deviance_diff_long, aes(x = Distribution, y = -deviance/2)) + 
+ll_plot = ggplot(deviance_diff_long, aes(x = Distribution, y = -deviance/2, fill = Distribution)) + 
   geom_hline(yintercept = 0) + 
   geom_violin() + 
   theme_bw() + 
+  scale_fill_manual(values = colors, guide = FALSE) +
   ylab("Deviation from mean log-likelihood")
 my_ggsave(name = "loglik.png", ll_plot)
 
-aic_plot = ggplot(AICc_diff_long, aes(x = Distribution, y = AICc)) + 
+aic_plot = ggplot(AICc_diff_long, aes(x = Distribution, y = AICc, fill = Distribution)) + 
   geom_hline(yintercept = 0) + 
   geom_violin() + 
   theme_bw() + 
+  scale_fill_manual(values = colors, guide = FALSE) +
   ylab("Deviation from mean AICc (lower is better)")
 my_ggsave(name = "aic.png", aic_plot)
 
@@ -212,16 +218,18 @@ AICc_weight_long = gather(AICc_weight,
 # Note: I had to tweak the bandwidth parameter for this plot, or zipf's splat at
 # zero would be so wide that the other distributions would be invisible by comparison.
 # A bandwidth much less than 0.01 on a 0-1 scale is probably undersmoothed anyway.
[…]

### 2016-11-10 peerj_response_letter.md

@@
 place for that level of detail is in the openly available code associated with
-an analysis. Our code is publicly available under open source licenses:
-https://github.com/weecology/sad-comparison and we will archive this repository
-on Zenodo as part of the publication of this paper. It can be run by anyone to
+an analysis. Our code is publicly available under open source licenses at
+https://github.com/weecology/sad-comparison and we have now archived it on
+Zenodo and added a link to this archive in the paper. It can be run by anyone to
 replicate our results and read to look up individual function use if desired.

### 2016-11-11 example-plot.py
Update Figure 1 color to match other figures

@@ -4,7 +4,7 @@ import macroeco_distributions as md
 from scipy.stats import zipf
 import matplotlib
 import matplotlib.pyplot as plt
-%matplotlib inline
+#%matplotlib inline
 
 # BBS 61036
 # fia site 14057000012
@@ -23,8 +23,9 @@ ab_array = np.array([[1L, 15L, 3L, 1L, 1L, 1L, 1L, 8L, 2L, 3L, 1L, 1L, 5L, 3L, 1
 4L, 1L, 1L, 9L, 3L, 8L, 3L, 2L, 10L, 4L, 14L, 4L, 2L, 3L, 1L,
 1L, 8L]])
 
-# Color Brewer's 3-class Dark2 colors, plus black
-colors = ["#000000", "#1b9e77", "#d95f02", "#7570b3"]
+# Color scheme from Dave Harris in
+# https://github.com/weecology/sad-comparison/issues/217
+colors = ["#990F0F", "#99700F", "#1F990F", "#710F99"]
 plot_labels = ["A", "B", "C"]
 
 fig_example = plt.figure(figsize = (12, 4))
@@ -74,4 +75,4 @@ for i in range(3):
     
 plt.tight_layout()
 plt.savefig('Fig1.pdf', dpi = 800)
-
+plt.savefig('Fig1.png', dpi = 800)

### 2016-11-11 peerj_response_letter.md
Add language about figure improvements to response letter

@@
 comments. Our responses are described in detail below.
+
+In addition to the recommended changes we have also worked on improving the
+figures. We have introduced a consistent, color-blind friendly, color scheme
+throughout to help the readers quickly recognize the different distributions on
+the different figures. We have also reworked Figure 4 somewhat extensively to
+both address Reviewer 2's concerns about font size but also improve the general
+appearance and communication of the figure more broadly.
 
@@
 
-We will work with PeerJ to make sure the sizes are appropriate should the paper
-be accepted.
+We have increased the label sizes on this figure and also worked to improve it
+more generally so that it will communicate well with the readers and be easy to
+view and understand on a printed pdf.
 
